% \clearpage
\subsection{Finishes}
The following option keys extend the options given in \Vref{subsec:skinfinish}.
There are no |app| type keys since finishes are stackable by default.

以下选项键扩展了 \Vref{subsec:skinfinish} 中给出的选项。默认情况下，饰面是可以堆叠的，因此没有 |app| 类型的键。
\begin{docTcbKey}{finish pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish}.

在 \refKeyLe{/tcb/finish} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish unbroken pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish unbroken}.

在 \refKeyLe{/tcb/finish unbroken} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish first pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish first}.

在 \refKeyLe{/tcb/finish first} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish middle pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish middle}.

在 \refKeyLe{/tcb/finish middle} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish last}.

在 \refKeyLe{/tcb/finish last} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish broken pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish broken}.

在 \refKeyLe{/tcb/finish broken} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish unbroken and first pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish unbroken and first}.

在 \refKeyLe{/tcb/finish unbroken and first} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish middle and last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish middle and last}.

在 \refKeyLe{/tcb/finish middle and last} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{finish unbroken and last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish unbroken and last}.

在 \refKeyLe{/tcb/finish unbroken and last} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-09-19]{finish first and middle pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/finish first and middle}.

在 \refKeyLe{/tcb/finish first and middle} 前面添加给定的 \meta{图形代码}。
\end{docTcbKey}