
\subsection{Embedding into the Surroundings\\嵌入到周围环境中}
The following option keys extend the options given in Subsection \ref{subsec:surroundings}
from page \pageref{subsec:surroundings}.

下面的选项键扩展了第 \ref{subsec:surroundings} 小节（第 \pageref{subsec:surroundings} 页）中给出的选项。
\begin{marker}
The \enquote{hookable} versions are usable inside the document.
In the preamble, they can only be used after explicit setting of
\refKeyLe{/tcb/before} and \refKeyLe{/tcb/after} or by e.\,g.\ \refKeyLe{/tcb/parskip}.

“hookable” 版本可以在文档内使用。
在导言区，它们只能在显式设置 \refKeyLe{/tcb/before} 和 \refKeyLe{/tcb/after} 或使用 \refKeyLe{/tcb/parskip} 等选项之后才能使用。
\end{marker}

\begin{docTcbKey}{before app}{=\meta{code}}{no default}
Appends the given \meta{code} to \refKeyLe{/tcb/before} before the colored box.

将给定的 \meta{code} 追加到 \refKeyLe{/tcb/before} 中，在彩色盒子之前。
\end{docTcbKey}

\begin{docTcbKey}{before pre}{=\meta{code}}{no default}
Prepends the given \meta{code} to \refKeyLe{/tcb/before} before the colored box.

将给定的 \meta{code} 前置到 \refKeyLe{/tcb/before} 中，在彩色盒子之前。
\end{docTcbKey}

\begin{docTcbKey}{after app}{=\meta{code}}{no default}
Appends the given \meta{code} to \refKeyLe{/tcb/after} after the colored box.

将给定的 \meta{code} 追加到 \refKeyLe{/tcb/after} 中，在彩色盒子之后。
\end{docTcbKey}

\begin{docTcbKey}{after pre}{=\meta{code}}{no default}
Prepends the given \meta{code} to \refKeyLe{/tcb/after} after the colored box.

将给定的 \meta{code} 前置到 \refKeyLe{/tcb/after} 中，在彩色盒子之后。
\end{docTcbKey}

% \begin{dispExample}
% \tcbset{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries}

% \begin{tcolorbox}[title=My title,before app={The box follows:\\[4pt]},
%   after app={This is the end.}]
% This is a \textbf{tcolorbox}.
% \end{tcolorbox}
% \end{dispExample}

\begin{dispExample}
\tcbset{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries}

\begin{tcolorbox}[title=我的标题,before app={The box follows:\\[4pt]},
  after app={This is the end.}]
This is a \textbf{tcolorbox}.
\end{tcolorbox}
\end{dispExample}
