

% \clearpage
\subsection{Underlays}
The following option keys extend the options given in \Vref{subsec:skinunderlay}.
There are no |app| type keys since underlays are stackable by default.

以下选项键扩展了 \Vref{subsec:skinunderlay} 中提供的选项。由于底纹默认是可堆叠的，因此没有 |app| 类型的键。
\begin{docTcbKey}{underlay pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay}。
\end{docTcbKey}

\begin{docTcbKey}{underlay unbroken pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay unbroken}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay unbroken}。
\end{docTcbKey}

\begin{docTcbKey}{underlay first pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay first}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay first}。
\end{docTcbKey}

\begin{docTcbKey}{underlay middle pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay middle}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay middle}。
\end{docTcbKey}

\begin{docTcbKey}{underlay last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay last}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay last}。
\end{docTcbKey}

\begin{docTcbKey}{underlay boxed title pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay boxed title}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay boxed title}。
\end{docTcbKey}

\begin{docTcbKey}{underlay broken pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay broken}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay broken}。
\end{docTcbKey}

\begin{docTcbKey}{underlay unbroken and first pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay unbroken and first}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay unbroken and first}。
\end{docTcbKey}

\begin{docTcbKey}{underlay middle and last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay middle and last}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay middle and last}。
\end{docTcbKey}

\begin{docTcbKey}{underlay unbroken and last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay unbroken and last}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay unbroken and last}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-09-19]{underlay first and middle pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/underlay first and middle}.

将给定的 \meta{graphical code} 前置到 \refKeyLe{/tcb/underlay first and middle}。
\end{docTcbKey}
