

\subsection{Overlays\\覆盖}
The following option keys extend the options given in Subsection \ref{subsec:overlays}
from page \pageref{subsec:overlays}.

下面的选项键扩展了第 \ref{subsec:overlays} 小节（第 \pageref{subsec:overlays} 页）中给出的选项。
\begin{docTcbKey}{overlay app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay}.

将给定的 \meta{graphical code} 追加到 \refKeyLe{/tcb/overlay} 中。
\begin{dispExample}
% \usetikzlibrary{patterns} % preamble
% \tcbuselibrary{skins} % preamble
\tcbset{frogbox/.style={enhanced,colback=green!10,colframe=green!65!black,
  enlarge top by=5.5mm,
  overlay={\foreach \x in {2cm,3.5cm} {
    \begin{scope}[shift={([xshift=\x]frame.north west)}]
      \path[draw=green!65!black,fill=green!10,line width=1mm] (0,0) arc (0:180:5mm);
      \path[fill=black] (-0.2,0) arc (0:180:1mm);
    \end{scope}}}}}
\tcbset{ribbon/.style={overlay app={%
  \path[fill=blue!75!white,draw=blue,double=white!85!blue,
    preaction={opacity=0.6,fill=blue!75!white},
    line width=0.1mm,double distance=0.2mm,
    pattern=fivepointed stars,pattern color=white!75!blue]
    ([xshift=-0.2mm,yshift=-1.02cm]frame.north east)
    -- ++(-1,1) -- ++(-0.5,0) -- ++(1.5,-1.5) -- cycle;}}}

\begin{tcolorbox}[frogbox,title=My title]
This is a \textbf{tcolorbox}.
\end{tcolorbox}

\begin{tcolorbox}[frogbox,ribbon,title=My title]
This is a \textbf{tcolorbox}.\par
Here, we apply a second overlay.
\end{tcolorbox}
\end{dispExample}
\end{docTcbKey}

\begin{docTcbKey}{overlay pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay}.

在 \refKeyLe{/tcb/overlay} 前插入给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay unbroken app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay unbroken}.

在 \refKeyLe{/tcb/overlay unbroken} 后附加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay unbroken pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay unbroken}.

在 \refKeyLe{/tcb/overlay unbroken} 前插入给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay first app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay first}.

在 \refKeyLe{/tcb/overlay first} 后附加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay first pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay first}.

在 \refKeyLe{/tcb/overlay first} 前插入给定的 \meta{图形代码}。
\end{docTcbKey}

% \clearpage
\begin{docTcbKey}{overlay middle app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay middle}.

在 \refKeyLe{/tcb/overlay middle} 后附加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay middle pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay middle}.

在 \refKeyLe{/tcb/overlay middle} 前插入给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay last app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay last}.

在 \refKeyLe{/tcb/overlay last} 后附加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay last}.

在 \refKeyLe{/tcb/overlay last} 前插入给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay broken app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay broken}.

在 \refKeyLe{/tcb/overlay broken} 后附加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay broken pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay broken}.

在 \refKeyLe{/tcb/overlay broken} 前插入给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay unbroken and first app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay unbroken and first}.

在 \refKeyLe{/tcb/overlay unbroken and first} 后附加给定的 \meta{图形代码}。
\end{docTcbKey}

\begin{docTcbKey}{overlay unbroken and first pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay unbroken and first}.

将给定的 \meta{图形代码} 添加到 \refKeyLe{/tcb/overlay unbroken and first} 的前面。
\end{docTcbKey}

\begin{docTcbKey}{overlay middle and last app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay middle and last}.

将给定的 \meta{图形代码} 添加到 \refKeyLe{/tcb/overlay middle and last} 的后面。
\end{docTcbKey}

\begin{docTcbKey}{overlay middle and last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay middle and last}.

将给定的 \meta{图形代码} 添加到 \refKeyLe{/tcb/overlay middle and last} 的前面。
\end{docTcbKey}

\begin{docTcbKey}{overlay unbroken and last app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay unbroken and last}.

将给定的 \meta{图形代码} 添加到 \refKeyLe{/tcb/overlay unbroken and last} 的后面。
\end{docTcbKey}

\begin{docTcbKey}{overlay unbroken and last pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay unbroken and last}.

将给定的 \meta{图形代码} 添加到 \refKeyLe{/tcb/overlay unbroken and last} 的前面。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-09-19]{overlay first and middle app}{=\meta{graphical code}}{no default}
Appends the given \meta{graphical code} to \refKeyLe{/tcb/overlay first and middle}.

将给定的 \meta{图形代码} 添加到 \refKeyLe{/tcb/overlay first and middle} 的后面。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-09-19]{overlay first and middle pre}{=\meta{graphical code}}{no default}
Prepends the given \meta{graphical code} to \refKeyLe{/tcb/overlay first and middle}.

将给定的 \meta{图形代码} 添加到 \refKeyLe{/tcb/overlay first and middle} 的前面。
\end{docTcbKey}
