\subsection{Extras}
The following option keys extend the options given in \Vref{subsec:extras}.
There are no |app| type keys since extras are stackable by default.

以下选项扩展了\Vref{subsec:extras}中给出的选项。默认情况下，不存在类型为|app|的键，因为额外选项默认可以叠加。
\begin{docTcbKey}[][doc new=2015-07-16]{extras pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras}.

在 \refKeyLe{/tcb/extras} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras unbroken pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras unbroken}.

在 \refKeyLe{/tcb/extras unbroken} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras first pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras first}.

在 \refKeyLe{/tcb/extras first} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras middle pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras middle}.

在 \refKeyLe{/tcb/extras middle} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras last pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras last}.

在 \refKeyLe{/tcb/extras last} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras broken pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras broken}.

在 \refKeyLe{/tcb/extras broken} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras unbroken and first pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras unbroken and first}.

在 \refKeyLe{/tcb/extras unbroken and first} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras middle and last pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras middle and last}.

在 \refKeyLe{/tcb/extras middle and last} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras unbroken and last pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras unbroken and last}.

在 \refKeyLe{/tcb/extras unbroken and last} 前加上给定的 \meta{options}。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2015-07-16]{extras first and middle pre}{=\marg{options}}{无默认值}
Prepends the given \meta{options} to \refKeyLe{/tcb/extras first and middle}.

在 \refKeyLe{/tcb/extras first and middle} 前加上给定的 \meta{options}。
\end{docTcbKey}
