In theory, \tikzname\ itself is just one of several possible ``frontends''.
which are sets of commands or a special syntax that makes using the basic layer
easier. A problem with directly using the basic layer is that code written for
this layer is often too ``verbose''. For example, to draw a simple triangle,
you may need as many as five commands when using the basic layer: One for
beginning a path at the first corner of the triangle, one for extending the
path to the second corner, one for going to the third, one for closing the
path, and one for actually painting the triangle (as opposed to filling it).
With the \tikzname\ frontend all this boils down to a single simple
\textsc{metafont}-like command:

理论上，\tikzname\ 本身只是几种可能的“前端”之一，这些前端是一组命令或一种特殊语法，使得使用基础层更加容易。直接使用基础层的问题在于，为这一层编写的代码通常过于“冗长”。例如，要画一个简单的三角形，你可能需要使用基础层的五个命令：一个用于在三角形的第一个角开始一条路径，一个用于将路径延伸到第二个角，一个用于去到第三个角，一个用于关闭路径，以及一个用于实际绘制三角形（而不是填充它）。使用 \tikzname\ 前端，所有这些都可以简化为一个简单的 \textsc{metafont} 类似的命令：
%
\begin{verbatim}
\draw (0,0) -- (1,0) -- (1,1) -- cycle;
\end{verbatim}

In practice, \tikzname\ is the only ``serious'' frontend for \pgfname. It gives
you access to all features of \pgfname, but it is intended to be easy to use.
The syntax is a mixture of \textsc{metafont} and \textsc{pstricks} and some
ideas of myself. There are other frontends besides \tikzname, but they are intended
more as ``technology studies'' and less as serious alternatives to
\tikzname. In particular, the |pgfpict2e| frontend   reimplements the standard
\LaTeX\ |{picture}|  environment and commands like |\line| or |\vector| using
the \pgfname\ basic layer. This layer is not really ``necessary'' since the
|pict2e.sty| package does at least as good a job at reimplementing the
|{picture}| environment. Rather, the idea behind this package is to have a
simple demonstration of how a frontend can be implemented.

在实践中,\tikzname\ 是\pgfname 的唯一“严肃的”前端。它为您提供了\pgfname 的所有功能,但旨在易于使用。其语法是\textsc{metafont}和\textsc{pstricks}以及我自己的一些想法的混合。除了\tikzname\ 之外还有其他前端,但它们的目的更多是作为“技术研究”,而不是作为\tikzname 的真正替代品。特别是,|pgfpict2e|前端使用\pgfname 基本层重新实现了标准\LaTeX|{picture}|环境和|\line|或|\vector|等命令。这个层次并不是真的“必要的”,因为|pict2e.sty|包至少和重新实现|{picture}|环境一样出色。相反,这个包背后的想法是展示一个前端如何实现的简单演示。

% 实际上，\tikzname\ 是 \pgfname\ 唯一的“严肃”前端。它使你能够访问 \pgfname\ 的所有功能，但它旨在易于使用。其语法是 \textsc{metafont} 和 \textsc{pstricks} 的混合，以及一些我自己的想法。除了 \tikzname\ 之外还有其他前端，但它们更像是“技术研究”而不是 \tikzname\ 的严肃替代品。特别是，|pgfpict2e| 前端使用 \pgfname\ 基础层重新实现了标准的 \LaTeX\ |{picture}| 环境以及像 |\line| 或 |\vector| 这样的命令。这个层次并不真正“必要”，因为 |pict2e.sty| 包至少能做得和重新实现 |{picture}| 环境一样好。相反，这个包背后的理念是展示如何可以实现一个前端。



Since most users will only use \tikzname\ and almost no one will use the system
layer directly, this manual is mainly about \tikzname\ in the first parts; the
basic layer and the system layer are explained at the end.

由于大多数用户只会使用\tikzname ,几乎没有人会直接使用系统层,所以在前面部分这本手册主要关于\tikzname ;基本层和系统层在后面解释。

% 由于大多数用户只会使用 \tikzname\，几乎没有人会直接使用系统层，所以这个手册的主要内容是关于 \tikzname\ 的第一部分；基础层和系统层在最后解释。



我2 3
\end{document}


\subsection{Comparison with Other Graphics Packages}

\tikzname\ is not the only graphics package for \TeX. In the following, I try
to give a reasonably fair comparison of \tikzname\ and other packages.
%
\begin{enumerate}
    \item The standard \LaTeX\ |{picture}| environment allows you to create
        simple graphics, but little more. This is certainly not due to a lack
        of knowledge or imagination on the part of \LaTeX's designer(s).
        Rather, this is the price paid for the |{picture}| environment's
        portability: It works together with all backend drivers.
    \item The |pstricks| package is certainly powerful enough to create any
        conceivable kind of graphic, but it is not really portable. Most
        importantly, it does not work with |pdftex| nor with any other driver
        that produces anything but PostScript code.

        Compared to \tikzname, |pstricks| has a similar support base. There
        are many nice extra packages for special purpose situations that have
        been contributed by users over the last decade. The \tikzname\ syntax
        is more consistent than the |pstricks| syntax as \tikzname\ was
        developed ``in a more centralized manner'' and also ``with the
        shortcomings on |pstricks| in mind''.
    \item The |xypic| package is an older package for creating graphics.
        However, it is more difficult to use and to learn because the syntax
        and the documentation are a bit cryptic.
    \item The |dratex| package is a small graphic package for creating a
        graphics. Compared to the other package, including \tikzname, it is
        very small, which may or may not be an advantage.
    \item The |metapost| program is a powerful alternative to \tikzname. It
        used to be an external program, which entailed a bunch of problems,
        but in Lua\TeX\ it is now built in. An obstacle with |metapost| is
        the inclusion of labels. This is \emph{much} easier to achieve using
        \pgfname.
    \item The |xfig| program is an important alternative to \tikzname\ for
        users who do not wish to ``program'' their graphics as is necessary
        with \tikzname\ and the other packages above. There is a conversion
        program that will convert |xfig| graphics to \tikzname.
\end{enumerate}


\subsection{Utility Packages}

The \pgfname\ package comes along with a number of utility package that are not
really about creating graphics and which can be used independently of \pgfname.
However, they are bundled with \pgfname, partly out of convenience, partly
because their functionality is closely intertwined with \pgfname. These utility
packages are:
%
\begin{enumerate}
    \item The |pgfkeys| package defines a powerful key management facility.
        It can be used completely independently of \pgfname.
    \item The |pgffor| package defines a useful |\foreach| statement.
    \item The |pgfcalendar| package defines macros for creating calendars.
        Typically, these calendars will be rendered using \pgfname's graphic
        engine, but you can use |pgfcalendar| also typeset calendars using
        normal text. The package also defines commands for ``working'' with
        dates.
    \item The |pgfpages| package is used to assemble several pages into a
        single page. It provides commands for assembling several ``virtual
        pages'' into a single ``physical page''. The idea is that whenever
        \TeX\ has a page ready for ``shipout'', |pgfpages| interrupts this
        shipout and instead stores the page to be shipped out in a special
        box. When enough ``virtual pages'' have been accumulated in this way,
        they are scaled down and arranged on a ``physical page'', which then
        \emph{really} shipped out. This mechanism allows you to create ``two
        page on one page'' versions of a document directly inside \LaTeX\
        without the use of any external programs. However, |pgfpages| can do
        quite a lot more than that. You can use it to put logos and watermark
        on pages, print up to 16 pages on one page, add borders to pages, and
        more.
\end{enumerate}


\subsection{How to Read This Manual}

This manual describes both the design of \tikzname\ and its usage. The
organization is very roughly according to ``user-friendliness''. The commands
and subpackages that are easiest and most frequently used are described first,
more low-level and esoteric features are discussed later.

If you have not yet installed \tikzname, please read the installation first.
Second, it might be a good idea to read the tutorial. Finally, you might wish
to skim through the description of \tikzname. Typically, you will not need to
read the sections on the basic layer. You will only need to read the part on
the system layer if you intend to write your own frontend or if you wish to
port \pgfname\ to a new driver.

The ``public'' commands and environments provided by the system are described
throughout the text. In each such description, the described command,
environment or option is printed in red. Text shown in green is optional and
can be left out.


\subsection{Authors and Acknowledgements}
\label{section-authors}

The bulk of the \pgfname\ system and its documentation was written by Till
Tantau. A further member of the main team is Mark Wibrow, who is responsible,
for example, for the \pgfname\ mathematical engine, many shapes, the decoration
engine, and matrices. The third member is Christian Feuers\"anger who
contributed the floating point library, image externalization, extended key
processing, and automatic hyperlinks in the manual.

Furthermore, occasional contributions have been made by Christophe Jorssen,
Jin-Hwan Cho, Olivier Binda, Matthias Schulz, Ren\'ee Ahrens, Stephan Schuster,
and Thomas Neumann.

Additionally, numerous people have contributed to the \pgfname\ system by
writing emails, spotting bugs, or sending libraries and patches. Many thanks to
all these people, who are too numerous to name them all!


\subsection{Getting Help}

When you need help with \pgfname\ and \tikzname, please do the following:

\begin{enumerate}
    \item Read the manual, at least the part that has to do with your
        problem.
    \item If that does not solve the problem, try having a look at the
        GitHub development page for \pgfname\ and \tikzname\ (see the
        title of this document). Perhaps someone has already reported a
        similar problem and someone has found a solution.
    \item On the website you will find numerous forums for getting help.
        There, you can write to help forums, file bug reports, join mailing
        lists, and so on.
    \item Before you file a bug report, especially a bug report concerning
        the installation, make sure that this is really a bug. In particular,
        have a look at the |.log| file that results when you \TeX\ your
        files. This |.log| file should show that all the right files are
        loaded from the right directories. Nearly all installation problems
        can be resolved by looking at the |.log| file.
    \item \emph{As a last resort} you can try to email me (Till Tantau) or,
        if the problem concerns the mathematical engine, Mark Wibrow. I do
        not mind getting emails, I simply get way too many of them. Because
        of this, I cannot guarantee that your emails will be answered in a 
        timely fashion or even at all. Your chances that your problem will
        be fixed are somewhat higher if you mail to the \pgfname\ mailing
        list (naturally, I read this list and answer questions when I have
        the time).
\end{enumerate}
