\begin{marker}
The \mylib{listingsutf8} library is not needed (and troublesome) when using Xe\LaTeX\ or Lua\LaTeX.
Therefore, loading this library is automatically replaced by loading
\mylib{listings} only, if pdf\LaTeX\ is \emph{not} used.

当使用 Xe\LaTeX\ 或 Lua\LaTeX 时，不需要（而且可能会有问题）加载 \mylib{listingsutf8} 库。 因此，如果不使用 pdf\LaTeX，加载此库会自动替换为仅加载 \mylib{listings}。
\end{marker}

The \mylib{listingsutf8} library is an extension of the
\mylib{listings} library, so
all options from \Vref{sec:speclistingkeys} are applicable.

\mylib{listingsutf8} 库是 \mylib{listings} 库的扩展，因此 \Vref{sec:speclistingkeys} 中的所有选项都适用。
\begin{docTcbKey}{listing utf8}{=\meta{one-byte-encoding}}{style, no default, initially |latin1|}
Abbreviation for using \refKeyLe{/tcb/listing inputencoding}
together with UTF-8 support from the package |listingsutf8| .
This option is available only for the library variant \mylib{listingsutf8}.
The \meta{one-byte-encoding} is one of
the applicable encodings from , e.\,g.\ |latin1|
which is the default.\par

% 使用\refKeyLe{/tcb/listing inputencoding}的缩写，结合来自包|listingsutf8|的UTF-8支持。此选项仅适用于库变体\mylib{listingsutf8}。\meta{one-byte-encoding}是来自的适用编码之一，例如|latin1|是默认值。

使用\refKeyLe{/tcb/listing inputencoding}和来自|listingsutf8|包的UTF-8支持的缩写。此选项仅适用于库变体\mylib{listingsutf8}。 \meta{one-byte-encoding} 是可适用的编码之一，例如|latin1|是默认值。

Be aware that this means restriction to this specific \meta{one-byte-encoding}:
e.\,g.\ |latin1| comprises umlauts and other accented characters, but not
the Euro sign. If you want to use the |listings| package \emph{and} \flqq real\frqq\
UTF-8 source code, then do \emph{not} use \mylib{listingsutf8} but \mylib{listings}
with
\refKeyLe{/tcb/listing inputencoding}|=utf8|
\emph{and} with specific manual hacks for specific UTF-8-encoded characters.

% 请注意，这意味着限制在特定的\meta{one-byte-encoding}上：例如|latin1|包括umlauts和其他重音字符，但不包括欧元符号。如果您想同时使用|listings|包和“真正的”UTF-8源代码，则不要使用\mylib{listingsutf8}，而是使用\mylib{listings}，并使用\refKeyLe{/tcb/listing inputencoding}|=utf8|以及针对特定UTF-8编码字符的手动修补。

请注意，这意味着限制于特定的 \meta{单字节编码}： 例如，|latin1| 包含变音符和其他有重音符号的字符，但不包括欧元符号。如果您想使用 |listings| 宏包并使用“真正”的 UTF-8 源代码，则不要使用 \mylib{listingsutf8}，而应该使用带有 \refKeyLe{/tcb/listing inputencoding}|=utf8| 的 \mylib{listings}，并且使用特定的手动修改来处理特定的 UTF-8 编码字符。
\end{docTcbKey}

See further options in \Vref{sec:commonlistingkeys}.

请参阅 \Vref{sec:commonlistingkeys} 中的其他选项。