\SaveVerb{vTmpVerbOne}{including \documentclass, \begin{document} and \end{document}}%\texttt{SaveVerb}命令是在\texttt{fancyvrb}宏包中定义的

A %
\makebox[0pt][l]{\raisebox{1em}{~\UseVerb{vTmpVerbOne}}}
complete \LaTeX\ document
cannot be processed directly by |tcolorbox|%(including |\documentclass|, |\begin{document}| and |\end{document}|)
.
It always has to be compiled separately. There are two methods supported
by the package to process and display such a full document example:%

% 包括 |\documentclass|、|\begin{document}| 和 |\end{document}| 的完整 \LaTeX\ 文档不能直接由 |tcolorbox| 处理。 它必须单独编译。该包支持两种方法来处理和显示这样的完整文档示例： 

一个完整 \LaTeX\ 文档不能直接由 |tcolorbox| 处理%(包括 |\documentclass|、|\begin{document}| 和 |\end{document}|)
。它必须被单独编译。本包支持两种方法来处理和展示这样一个完整的文档示例：
\begin{itemize}
\item Prepare and compile the example document independent from your main
document. The source file and the resulting PDF file can be included
into the main document afterwards. This is the most economic way since
the example document can be left untouched after the example is complete.
\\独立于主文档准备和编译示例文档。源文件和生成的 PDF 文件可以随后包含到主文档中。这是最经济的方法，因为示例文档在示例完成后可以保持不变。
\item The other possibility is to compile the example on the fly while
the main document is compiled. This way has some charm, because the
example can be edited inside the main document. But be aware that the
compilation of the example is issued on every run of the main document.
Also, there are fewer degrees of freedom how the example is compiled.
\\另一种可能性是在编译主文档时即时编译示例。这种方式具有一些魅力，因为示例可以在主文档中进行编辑。但是请注意，示例的编译会在每次主文档运行时发出。此外，关于如何编译示例的自由度更少。
\end{itemize}
% \begin{itemize} \item  \item  \end{itemize}

For both methods, the resulting %example 
PDF file can be included
as a \refKey{/tcb/pdf comment}.

这两种方法生成的示例PDF文件,可以用\refKeyLe{/tcb/pdf comment}包含。