\begin{docCommand}{newtcblisting}{\oarg{init options}\marg{name}\oarg{number}\oarg{default}\marg{options}}
Creates a new environment \meta{name} based on \refEnvLe{tcblisting}.
Basically, |\newtcblisting| operates like |\newenvironment|. This means,
the new environment \meta{name} optionally takes \meta{number} arguments, where
\meta{default} is the default value for the optional first argument.
The \meta{options} are given to the underlying |tcblisting|.
Note that \refKeyLe{/tcb/savedelimiter} is set to the given \meta{name}
automatically.
The \meta{init options} allow setting up automatic numbering,
see Section \ref{sec:initkeys} from page \pageref{sec:initkeys}.

创建基于\refEnvLe{tcblisting}的新环境\meta{name}。 基本上，|\newtcblisting|的操作类似于|\newenvironment|。这意味着，新环境\meta{name}可以选择性地接受\meta{number}个参数，其中\meta{default}是可选第一个参数的默认值。 \meta{options}应用于底层的|tcblisting|。请注意，\refKeyLe{/tcb/savedelimiter}会自动设置为给定的\meta{name}。 \meta{init options}可用于设置自动编号，参见第\pageref{sec:initkeys}页的第\ref{sec:initkeys}节。
% \begin{dispExample*}{sbs,lefthand ratio=0.5}
% \newtcblisting{mybox}{%
% colback=red!5!white,
% colframe=red!75!black}

% \begin{mybox}
% This is my \LaTeX\ box.
% \end{mybox}
% \end{dispExample*}
\begin{dispExample*}{sbs,lefthand ratio=0.5}
\newtcblisting{mybox}{}
\begin{mybox}
This is my \LaTeX\ box.
\end{mybox}
\end{dispExample*}

% \begin{dispExample*}{sbs,lefthand ratio=0.5}
% \newtcblisting{mybox}[1]{%
% colback=red!5!white,
% colframe=red!75!black,
% fonttitle=\bfseries,
% title={#1}}

% \begin{mybox}{Listing Box}
% This is my \LaTeX\ box.
% \end{mybox}
% \end{dispExample*}
\begin{dispExample*}{sbs,lefthand ratio=0.5}
\newtcblisting{mybox}[1]{%
title={#1}}
\begin{mybox}{拥有一个标题参数}
This is my \LaTeX\ box.
\end{mybox}
\end{dispExample*}

% \begin{dispExample*}{sbs,lefthand ratio=0.5}
% \newtcblisting{mybox}[2][]{%
% colback=red!5!white,
% colframe=red!75!black,
% fonttitle=\bfseries,
% title={#2},#1}

% \begin{mybox}[listing only]
% {Listing Box}
% This is my \LaTeX\ box.
% \end{mybox}
% \bigskip

% \begin{mybox}[listing side text]
% {Listing Box}
% This is my
% \LaTeX\ box.
% \end{mybox}
% \end{dispExample*}
\begin{dispExample*}{sbs,lefthand ratio=0.6}
\newtcblisting{mybox}[2][]{title={#2},#1}
\begin{mybox}[listing only]{第二个参数是标题}
我的 \LaTeX\ 盒子。
\end{mybox}
\bigskip

\begin{mybox}[listing side text]{第一参数可选}
\LaTeX\
\end{mybox}
\end{dispExample*}

% \clearpage
\inputpreamblelisting{C}

\begin{dispExample*}{sbs,lefthand ratio=0.5}
\begin{mycbox}{Listing Box}
我的 \LaTeX\
\end{mycbox}
\end{dispExample*}
\end{docCommand}


%\enlargethispage*{1cm}
\begin{docCommand}{renewtcblisting}{\oarg{init options}\marg{name}\oarg{number}\oarg{default}\marg{options}}
Operates like \refComLe{newtcblisting}, but based on |\renewenvironment|% instead of |\newenvironment|
.An existing environment is redefined.

类似于 \refComLe{newtcblisting}，但是基于 |\renewenvironment|。% 而非 |\newenvironment| 运行。 
已有的环境将被重新定义。
\end{docCommand}