%% \clearpage
\begin{docEnvironment}[doclang/environment content=key description,doc updated=2020-04-22]
  {docKey}{\oarg{key path}\oarg{options}\marg{name}\marg{parameters}\marg{description}}
Documents a key with given \meta{name} and an optional \meta{key path}.
The given \meta{options} are set with \refCom{tcbset}.
This key takes mandatory or optional \meta{parameters} as value
with a short \meta{description}.
It is automatically indexed and can be referenced with
\refCom{refKey}\marg{name}.

记录一个带有给定的 \meta{name} 和可选的 \meta{key path} 的关键字。 给定的 \meta{options} 由 |\tcbset| 设置。 该关键字以强制或可选的 \meta{parameters} 作为值， 并带有简短的 \meta{description}。 它会自动索引，并可以通过 |\refKey|\marg{name} 引用。
\begin{dispExample}
\begin{docKey}[foo]{footitle}{=\meta{text}}{no default, initially empty}
Creates a heading line with \meta{text} as content.
\end{docKey}
\end{dispExample}
\end{docEnvironment}


\begin{docEnvironment}[doclang/environment content=key description,doc updated=2020-04-22]
  {docKey*}{\oarg{key path}\oarg{options}\marg{name}\marg{parameters}\marg{description}}
Identical to \refEnv{docKey}, but without index entry.

与 \refEnv{docKey} 相同，但没有索引条目。
\end{docEnvironment}

\begin{docEnvironment}[doclang/environment content=key description,doc new=2020-04-22]
  {docKeys}{\oarg{options}\brackets{\marg{variant1},\marg{variant2},...}}
Documents several (similar) key variants simultaneously.
The given \meta{options} are set with \refCom{tcbset} and are valid for
all variants and the documentation text.
Every variant is described by an option set \meta{variant1}, \meta{variant2}, and so on.
The most crucial options are
\refKeyLe{/tcb/doc keypath}, \refKeyLe{/tcb/doc name}, \refKeyLe{/tcb/doc parameter},
and \refKeyLe{/tcb/doc description}.

同时记录几个（相似的）关键变量。 给定的\meta{options}是通过|\tcbset|设置的，对所有变量和文档文本有效。 每个变量由一个选项集\meta{variant1}，\meta{variant2}等描述。 最关键的选项是|/tcb/doc keypath|，|/tcb/doc name|，|/tcb/doc parameter|和|/tcb/doc description|。
\begin{dispExample}
\begin{docKeys}[
  doc no index,   %  no index entries for this example
  doc keypath   = mykeyroot,
  doc parameter = {=\meta{length}},
]
{
  {
    doc name        = width,
    doc description = initially \texttt{10cm},
  },
  {
    doc name        = height,
    doc description = initially \texttt{7cm},
  },
}
example
\end{docKeys}
\end{dispExample}
\end{docEnvironment}

