\begin{docCommand}[doc new=2014-09-19]{tcbdocmarginnote}{\oarg{options}\marg{text}}
Creates a |tcolorbox| note with the given \meta{text} inside the margin using
the |marginnote| package. The style of the |tcolorbox| is predefined and can be
altered by \refKeyLe{/tcb/doc marginnote} and the given \meta{options}.

使用|marginnote|包，在边距内创建一个带有给定\meta{text}的|tcolorbox|注释。|tcolorbox|的样式是预定义的，可以通过\refKeyLe{/tcb/doc marginnote}和给定的\meta{options}进行修改。
\begin{dispExample}
Some text\tcbdocmarginnote{Note A}
which is commented by a note inside the margin.
Alternatively to |\tcbdocmarginnote|, you can always use
|\marginnote| with a |tcolorbox| directly.\par
This is further text%
\tcbdocmarginnote[colframe=blue!50!white,colback=blue!5!white]{Note B}
with another note.
\end{dispExample}
\end{docCommand}

\begin{docCommand}[doc new=2014-09-19]{tcbdocnew}{\marg{date}}
Auxiliary macro which typesets the \refKeyLe{/tcb/doclang/new} text with
the given \meta{date}. It may be redefined for customization.

辅助宏，用于使用给定的\meta{date}排版\refKeyLe{/tcb/doclang/new}文本。它可以重新定义以进行自定义。 

\makeatletter\renewcommand*{\tcbdocnew}[1]{\kvtcb@text@new: #1}\makeatother%
\begin{dispExample*}{sidebyside}
\tcbdocnew{1981-10-29}.
% Next one is displayed in the margin:
\tcbdocmarginnote{\tcbdocnew{1978-02-09}}
\end{dispExample*}
\end{docCommand}

\begin{docCommand}[doc new=2014-09-19]{tcbdocupdated}{\marg{date}}
Auxiliary macro which typesets the \refKeyLe{/tcb/doclang/updated} text with
the given \meta{date}. It may be redefined for customization.

辅助宏，用于使用给定的\meta{date}排版\refKeyLe{/tcb/doclang/updated}文本。它可以重新定义以进行定制。

\makeatletter\renewcommand*{\tcbdocupdated}[1]{\kvtcb@text@updated: #1}\makeatother%
\begin{dispExample*}{sidebyside}
\tcbdocupdated{2014-09-19}.
\end{dispExample*}
\end{docCommand}