%%\clearpage
\begin{docCommand}[doc updated=2020-04-22]{tcbmakedocSubKey}{\marg{name}\marg{key path}}
Creates a new environment \meta{name} based on \refEnv{docKey} for the
documentation of keys with the given \meta{key path} as root.
The new environment \meta{name} takes the same para\-meters as \refEnv{docKey} itself.
A second starred environment \meta{name} is also created, which is identical
to \meta{name} but without index entry.

基于给定的\meta{key path}作为根，为键的文档创建一个新的环境\meta{name}，基于\refEnv{docKey}。 新环境\meta{name}与\refEnv{docKey}本身具有相同的参数。 还创建了一个第二个带星号的环境\meta{name}，它与\meta{name}相同，但没有索引条目。
\begin{dispExample}
\tcbmakedocSubKey{docFooKey}{foo}

\begin{docFooKey}{foodummy}{=\meta{nothing}}{no default, initially empty}
Some key.
\end{docFooKey}

\begin{docFooKey*}{foo another dummy}{=\meta{nothing}}{no default, initially empty}
Some key (not indexed).
\end{docFooKey*}
\end{dispExample}
\end{docCommand}


\begin{docCommand}[doc new=2020-04-22]{tcbmakedocSubKeys}{\marg{name}\marg{key path}}
Creates a new environment \meta{name} based on \refEnv{docKeys} for the
documentation of keys with the given \meta{key path} as root.
The new environment \meta{name} takes the same para\-meters as \refEnv{docKeys} itself.

根据给定的\meta{键路径}，为键的文档创建一个基于\refEnv{docKeys}的新环境\meta{name}。新环境\meta{name}与\refEnv{docKeys}本身具有相同的参数。
\begin{dispExample}
\tcbmakedocSubKeys{docFooKeys}{foo}

\begin{docFooKeys}[
  doc parameter   = {=\meta{nothing}},
  doc description = {no default, initially empty},
]
{
  {
    doc name = foodummy 2,
  },
  {
    doc name = foo another dummy 2,
    doc no index,
  }
}
Some description.
\end{docFooKeys}
\end{dispExample}
\end{docCommand}