
\columnratio{0.55}
\begin{paracol}{2}
\subsubsection{Form Feed Character}
\label{sec:usage-var-ff}
\switchcolumn
\subsubsection{换页符}

\switchcolumn[0]*
\DescribeMacro{\VVBprintFF}
\DescribeMacro{\VVBprintFFas}
You might have found that |<FF>| (or |^L|) in |verbatim| caused a
mysterious error;
\begin{iverbatim}
! Forbidden control sequence found while scanning use of \@xverbatim.
\end{iverbatim}
\switchcolumn
您可能发现在|verbatim|中使用的|<FF>|（或|^L|）会导致一个神秘的错误；
\begin{iverbatim}
! Forbidden control sequence found while scanning use of \@xverbatim.
\end{iverbatim}

\switchcolumn[0]*
This is because |<FF>| is not {\em verbatimized}.  Giving the command
|\VVBprintFF| to $\langle$\textit{beg-def-}\allowbreak
\textit{outer}$\rangle$ (or \meta{beg-def-inner}) of |\newverbatim| does
it for you and makes |<FF>| printed as |^L| in default.  You may change
this default print image by;

\begin{quote}
|\VVBprintFFas|\Meta{str}
\end{quote}
\switchcolumn
这是因为|<FF>|没有被{\em verbatimized}。给出|\VVBprintFF|命令到$\langle$\textit{beg-def-}\allowbreak
\textit{outer}$\rangle$（或\meta{beg-def-inner}）中的|\newverbatim|可以为您完成这个操作，并且默认情况下将|<FF>|打印为|^{L}|。您可以通过以下方式更改此默认打印图像；
\begin{quote}
|\VVBprintFFas|\Meta{str}
\end{quote}

\switchcolumn[0]*
where \meta{str} is a sequence of any printable characters other than |{|
and |}|.  Note that this command is very {\em fragile} as |\verb| and
|\index|, and thus should not be used in an argument of other commands
including |\(re)newverbatim|.
\switchcolumn
其中\meta{str}是除了|{|和|}|之外的任何可打印字符的序列。请注意，此命令非常{\em 脆弱}，就像|\verb|和|\index|一样，因此不应在其他命令的参数中使用，包括|\(re)newverbatim|。

\switchcolumn[0]*
\DescribeMacro{\VVBbreakatFF}
\DescribeMacro{\VVBbreakatFFonly}
The other way to make |<FF>| acceptable is to give it a useful and natural
job, i.e.\ page breaking.  This is done by giving |\VVBbreakatFF| to
\meta{beg-def-inner} (not {\em outer}).  Its more powerful relative,
|\VVBbreakatFFonly|, is also available to allow page breaking at |<FF>|
only.  Unfortunately, these two commands are incompatible with
|\(re)newtabverbatim| and thus you have to use |\(re)newverbatim| with
|\VVBbegintab| {\em followed by} them.
\switchcolumn
另一种使 |<FF>| 可接受的方法是给它一个有用和自然的任务，即分页。这是通过将 |\VVBbreakatFF| 给予 \meta{beg-def-inner}（而不是 {\em outer}）来实现的。它的更强大的形式 |\VVBbreakatFFonly| 也可用于仅在 |<FF>| 处分页。不幸的是，这两个命令与 |(re)newtabverbatim| 不兼容，因此您必须使用 |(re)newverbatim| 与 |\VVBbegintab| {\em followed by} 它们。
\end{paracol}