
\subsection{Adding Styles for Specific Boxes\\为特定盒子添加样式}\label{subsec:raster_styles}

The following styles can be defined to address certain boxes inside
a \emph{raster}. Note that such style definitions are not removed by
\refKeyLe{/tcb/reset} or \refKeyLe{/tcb/raster reset}.
The style definitions are used in the order given below.

可以定义以下样式来处理 \emph{raster} 中的特定盒子。请注意，此类样式定义不会被 \refKeyLe{/tcb/reset} 或 \refKeyLe{/tcb/raster reset} 删除。样式定义按照以下顺序使用。
\begin{docTcbKey}[][doc new=2014-11-24]{raster every box}{}{style}
This style is used for every box.

此样式用于每个盒子。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-11-10]{raster odd column}{}{style}
This style is used for every box in an odd column.

此样式用于奇数列中的每个盒子。
\begin{dispExample}
\begin{tcbitemize}[size=small,colframe=red!50!black,colback=red!10!white,
raster odd column/.style={colframe=blue!50!black,colback=blue!10!white}]
\tcbitem One
\tcbitem Two
\tcbitem Three
\tcbitem Four
\end{tcbitemize}
\end{dispExample}
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-11-10]{raster even column}{}{style}
This style is used for every box in an even column.

这种样式适用于偶数列中的每个方框。
\end{docTcbKey}


\begin{docTcbKey}[][doc new=2014-11-10]{raster column n}{}{style}
This style is used for every box in the |n|-th column.
|n| has to be replaced by a number.

这种样式适用于第|n|列中的每个方框。 |n|必须替换为一个数字。
\end{docTcbKey}


\begin{docTcbKey}[][doc new=2014-11-10]{raster odd row}{}{style}
This style is used for every box in an odd row.

这种样式适用于奇数行中的每个方框。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-11-10]{raster even row}{}{style}
This style is used for every box in an even row.

这种样式适用于偶数行中的每个方框。
\end{docTcbKey}


\begin{docTcbKey}[][doc new=2014-11-10]{raster row m}{}{style}
This style is used for every box in the |m|-th row.
|m| has to be replaced by a number.

这种样式适用于第|m|行中的每个方框。 |m|必须替换为一个数字。
\begin{dispExample}
\begin{tcbitemize}[size=small,colframe=red!50!black,colback=red!10!white,
raster row 2/.style={colframe=blue!50!black,colback=blue!10!white}]
\tcbitem One
\tcbitem Two
\tcbitem Three
\tcbitem Four
\end{tcbitemize}
\end{dispExample}
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-11-10]{raster odd number}{}{style}
This style is used for every box with an odd number.

这种样式适用于每个奇数编号的方框。
\end{docTcbKey}

\begin{docTcbKey}[][doc new=2014-11-10]{raster even number}{}{style}
This style is used for every box with an even number.

这种样式适用于每个偶数编号的方框。
\begin{dispExample}
\begin{tcbitemize}[size=small,colframe=red!50!black,colback=red!10!white,
raster columns=3,
raster even number/.style={colframe=blue!50!black,colback=blue!10!white}]
\tcbitem One
\tcbitem Two
\tcbitem Three
\tcbitem Four
\tcbitem Five
\tcbitem Six
\end{tcbitemize}
\end{dispExample}
\end{docTcbKey}


\begin{docTcbKey}[][doc new=2014-11-10]{raster row m column n}{}{style}
This style is used for the box in the
|m|-th row and |n|-th column.
|m| and |n| have to be replaced by numbers.

这种样式用于第|m|行和第|n|列的方框。 其中|m|和|n|必须替换为数字。
\end{docTcbKey}


\begin{docTcbKey}[][doc new=2014-11-10]{raster number n}{}{style}
This style is used for the box with number |n|.
|n| has to be replaced by a number.

这种风格用于带有编号 |n| 的盒子。 |n| 必须由数字替换。
\begin{dispExample}
\begin{tcbitemize}[size=small,colframe=red!50!black,colback=red!10!white,
raster number 4/.style={colframe=blue!50!black,colback=blue!10!white}]
\tcbitem One
\tcbitem Two
\tcbitem Three
\tcbitem Four
\end{tcbitemize}
\end{dispExample}
\end{docTcbKey}


