The following keys are provided for language specific settings.
The English language is predefined.

以下键可用于设置特定语言。英语是预定义的。
\begin{docTcbKey}{english language}{}{style, no value}
将所有语言特定设置设置为英语。

Sets all language specific settings to English.
\end{docTcbKey}

\begin{langTcbKey}{color}{=\meta{text}}{no default, initially |color|}
用于颜色索引的文本。

Text used in the index for colors.
\end{langTcbKey}

\begin{langTcbKey}{colors}{=\meta{text}}{no default, initially |Colors|}
颜色索引中的标题文本。

Heading text in the index for colors.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2015-01-08}]{counter}{=\meta{text}}{no default, initially |counter|}
用于计数器索引的文本。

Text used in the index for counters.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2015-01-08}]{counters}{=\meta{text}}{no default, initially |Counters|}
计数器索引中的标题文本。

Heading text in the index for counters.
\end{langTcbKey}

\begin{langTcbKey}{environment}{=\meta{text}}{no default, initially |environment|}
用于环境索引的文本。

Text used in the index for environments.
\end{langTcbKey}

\begin{langTcbKey}{environments}{=\meta{text}}{no default, initially |Environments|}
环境索引中的标题文本。

Heading text in the index for environments.
\end{langTcbKey}

\begin{langTcbKey}{environment content}{=\meta{text}}{no default, initially |environment content|}
\refEnvLe{docEnvironment} 中使用的文本。

Text used in \refEnvLe{docEnvironment}.
\end{langTcbKey}

\begin{langTcbKey}{index}{=\meta{text}}{no default, initially |Index|}
索引的标题文本。

Heading text for the index.
\end{langTcbKey}

\begin{langTcbKey}{key}{=\meta{text}}{no default, initially |key|}
用于键索引的文本。

Text used in the index for keys.
\end{langTcbKey}

\begin{langTcbKey}{keys}{=\meta{text}}{no default, initially |Keys|}
用于键索引中的标题文本。

Heading text used in the index for keys.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2015-01-08}]{length}{=\meta{text}}{no default, initially |length|}
长度索引中使用的文本。

Text used in the index for lengths.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2015-01-08}]{lengths}{=\meta{text}}{no default, initially |Lengths|}
长度索引中的标题文本。

Heading text in the index for lengths.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2014-09-19}]{new}{=\meta{text}}{no default, initially |New|}
新内容的公告文本。

Announcement text for new content.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2019-09-18}]{path}{=\meta{text}}{no default, initially |path operation|}
路径操作索引中使用的文本。

Text used in the index for path operations.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2019-09-18}]{paths}{=\meta{text}}{no default, initially |Path operations|}
路径操作索引中的标题文本。

Heading text in the index for path operations.
\end{langTcbKey}

\begin{langTcbKey}{pageshort}{=\meta{text}}{no default, initially |P.|}
页面引用的简短文本。

Short text for page references.
\end{langTcbKey}

\begin{langTcbKey}[][doc new={2014-09-19}]{updated}{=\meta{text}}{no default, initially |Updated|}
更新内容的公告文本。

Announcement text for updated content.
\end{langTcbKey}

\begin{langTcbKey}{value}{=\meta{text}}{no default, initially |value|}
用于值索引的文本。

Text used in the index for values.
\end{langTcbKey}

\begin{langTcbKey}{values}{=\meta{text}}{no default, initially |Values|}
值的索引标题文本。

Heading text in the index for values.
\end{langTcbKey}