\section{Introduction\hfill 导言}

\columnratio{0.6}
\begin{paracol}{2}
To set dimensions for page layout in \LaTeX\ is not straightforward. 
You need to adjust several \LaTeX{} native dimensions to place a text area
where you want.
If you want to center the text area in the paper you use, for example, 
you have to specify native dimensions as follows:
\switchcolumn 
在 {\LaTeX} 中设置页面布局并不简单。
你需要调整几个 {\LaTeX} 的内部尺寸，以将文本区域放置在你想要的位置。
例如，如果你想要在纸张上居中显示文本区域，你需要指定以下内部尺寸：
% \switchcolumn
% \begin{quote}
% |\usepackage{calc}|\\
% |\setlength\textwidth{7in}|\\
% |\setlength\textheight{10in}|\\
% |\setlength\oddsidemargin{(\paperwidth-\textwidth)/2 - 1in}|\\
% |\setlength\topmargin{(\paperheight-\textheight|\\
% |                      -\headheight-\headsep-\footskip)/2 - 1in}|.
% \end{quote}
% \switchcolumn
\end{paracol}
\begin{minted}{latex}
\usepackage{calc}
\setlength\textwidth{7in}
\setlength\textheight{10in}
\setlength\oddsidemargin{(\paperwidth-\textwidth)/2 - 1in}
\setlength\topmargin{(\paperheight-\textheight-\headheight-\headsep-\footskip)/2 - 1in}
\end{minted}


\columnratio{0.55}
\begin{paracol}{2}
Without package \textsl{calc}, the above example would need
more tedious settings. Package \Gm\ provides an easy
way to set page layout parameters. In this case, what you have to do
is just
\begin{quote}
|\usepackage[text={7in,10in},centering]{geometry}|. 
\end{quote}
\switchcolumn
如果没有使用\textsl{calc}宏包，上面的示例将需要更繁琐的设置。宏包\Gm\ 提供了一种简便的方式来设置页面布局参数。在这种情况下，您只需要做以下操作：
\begin{minted}{latex}
\usepackage[text={7in,10in},centering]{geometry}
\end{minted}
\switchcolumn
Besides centering problem, setting margins from each edge of the paper is
also troublesome. But \Gm\ also make it easy.
If you want to set each margin to 1.5in, you can type
\begin{quote}
|\usepackage[margin=1.5in]{geometry}| 
\end{quote}
\switchcolumn
除了居中问题，设置页面边距也会变得麻烦。但是\Gm\ 也可以轻松解决这个问题。如果您想将每个边缘的边距设置为1.5英寸，可以输入：
\begin{minted}{latex}
\usepackage[margin=1.5in]{geometry}
\end{minted}
\switchcolumn
Thus, the geometry package has an auto-completion mechanism, in which
unspecified dimensions are automatically determined.
The \Gm\ package will be also useful when you have to set page layout
obeying the following strict instructions: for example,
\switchcolumn
因此，\Gm\ 宏包具有自动完成机制，未指定的尺寸将自动确定。当您需要按照严格的说明设置页面布局时，\Gm\ 宏包也非常有用。例如：

\switchcolumn[0]*
\begin{quote}\slshape
The total allowable width of the text area is $6.5$ inches wide by $8.75$
inches high. The top margin on each page should be $1.2$ inches from
the top edge of the page. The left margin should be $0.9$ inch from 
the left edge. The footer with page number should be at the bottom
of the text area.
\end{quote}
\switchcolumn
\begin{quote}\slshape
文本区域的总可允许宽度为6.5英寸，高度为8.75英寸。每页的顶部边距应距离页面顶部边缘1.2英寸。左边距应距离左边缘0.9英寸。页脚与页码应位于文本区域底部。
\end{quote}

\switchcolumn[0]*
In this case, using \Gm\ you can type
\begin{quote}
|\usepackage[total={6.5in,8.75in},|\\
|            top=1.2in, left=0.9in, includefoot]{geometry}|.
\end{quote}
\switchcolumn
在这种情况下，使用\Gm\ 宏包，您可以输入：
\begin{minted}{latex}
\usepackage[total={6.5in,8.75in},
top=1.2in, left=0.9in, includefoot]{geometry}
\end{minted}

\switchcolumn
Setting a text area on the paper in document preparation system has some
analogy to placing a window on the background in the window system. 
The name `geometry' comes from the |-geometry| option used for specifying
a size and location of a window in X Window System.
\switchcolumn
在文档准备系统中，设置纸张上的文本区域类似于在窗口系统中将窗口放置在背景上。``geometry''这个名称源于在X Window System中用于指定窗口大小和位置的|-geometry|选项。
\end{paracol}

