\section{User interface\hfill 用户接口}

\subsection{Commands\hfill 命令}

\columnratio{0.55}
\begin{paracol}{2}
The \Gm\ package provides the following commands:
\switchcolumn
\Gm\ 宏包提供以下命令：
\end{paracol}

\begin{itemize}\setlength{\itemsep}{-.5\parsep}
\columnratio{0.55}
\begin{paracol}{2}
\item |\geometry{|\meta{options}|}|
\switchcolumn
\item |\geometry{|\meta{options}|}|

\switchcolumn
\item |\newgeometry{|\meta{options}|}| and |\restoregeometry|
\switchcolumn
\item |\newgeometry{|\meta{options}|}| 和 |\restoregeometry|

\switchcolumn
\item |\savegeometry{|\meta{name}|}| and |\loadgeometry{|\meta{name}|}|
\switchcolumn
\item |\savegeometry{|\meta{name}|}| 和 |\loadgeometry{|\meta{name}|}|
\end{paracol}
\end{itemize}

% \columnratio{0.55}
% \begin{paracol}{2}
% The \Gm\ package provides the following commands:
% \begin{itemize}\setlength{\itemsep}{-.5\parsep}
% \item |\geometry{|\meta{options}|}|
% \item |\newgeometry{|\meta{options}|}| and |\restoregeometry|
% \item |\savegeometry{|\meta{name}|}| and |\loadgeometry{|\meta{name}|}|
% \end{itemize}
% \switchcolumn
% \Gm\ 宏包提供以下命令：
% \begin{itemize}\setlength{\itemsep}{-.5\parsep}
% \item |\geometry{|\meta{options}|}|
% \item |\newgeometry{|\meta{options}|}| 和 |\restoregeometry|
% \item |\savegeometry{|\meta{name}|}| 和 |\loadgeometry{|\meta{name}|}|
% \end{itemize}
% \end{paracol}

\columnratio{0.55}
\begin{paracol}{2}
|\geometry{|\meta{options}|}|
changes the page layout according to the options specified in the
argument. This command, if any, should be placed only in the
preamble (before |\begin{document}|).
\switchcolumn
|\geometry{|\meta{options}|}|根据参数中指定的选项更改页面布局。如果有的话，此命令应该只放在导言区（|\begin{document}|之前）。
%%%
\switchcolumn
The \Gm\ package may be used as part of a class or another package
you use in your document. The command \cs{geometry} can overwrite
some of the settings in the preamble. Multiple use of \cs{geometry}
is allowed and then processed with the options concatenated.
If \Gm\ is not yet loaded, you can use only
|\usepackage[|\meta{options}|]{geometry}| instead of \cs{geometry}.
\switchcolumn
\Gm\ 宏包可以作为文档中使用的类或其他宏包的一部分。命令\cs{geometry}可以覆盖导言区中的一些设置。可以多次使用\cs{geometry}命令，并将选项连接在一起进行处理。如果\Gm\ 尚未加载，可以使用|\usepackage[|\meta{options}|]{geometry}|代替\cs{geometry}。    
\switchcolumn
\medskip
|\newgeometry{|\meta{options}|}|
changes the page layout mid-document. \cs{newgeometry} is almost
similar to \cs{geometry} except that \cs{newgeometry} disables all
the options specified by \cs{usepackage} and \cs{geometry} in
the preamble and skips papersize-related options. 
\cs{restoregeometry}
restores the page layout specified in the preamble. This command
has no arguments. See Section~\ref{sec:midchange} for details.
\switchcolumn
\medskip
|\newgeometry{|\meta{options}|}|可以在文档中更改页面布局。\cs{newgeometry}与\cs{geometry}几乎相同,除了会禁用导言区中由\cs{usepackage}和\cs{geometry}指定的所有选项，并且跳过与页面尺寸相关的选项外。|\restoregeometry|命令将恢复导言区中指定的页面布局。此命令没有参数。详见第~\ref{sec:midchange} 节。
\switchcolumn[0]*
\medskip
|\savegeometry{|\meta{name}|}|
saves the page dimensions as \meta{name} where you put
this command.
|\loadgeometry{|\meta{name}|}|
loads the page dimensions saved as \meta{name}. See
Section~\ref{sec:midchange} for details.
\switchcolumn
\medskip
|\savegeometry{|\meta{name}|}|将页面尺寸保存为\meta{name}。
|\loadgeometry{|\meta{name}|}|加载保存为\meta{name}的页面尺寸。详见第~\ref{sec:midchange} 节。
\end{paracol}


\subsection{Optional argument\hfill 可选参数}

\columnratio{0.55}
\begin{paracol}{2}
The \Gm\ package adopts \textsf{keyval} interface
`\meta{key}=\meta{value}' for the optional argument to
\cs{usepackage}, \cs{geometry} and \cs{newgeometry}.
\switchcolumn
\Gm\ 宏包在\cs{usepackage}、\cs{geometry}和\cs{newgeometry}的可选参数中采用了\textsf{keyval}接口的`\meta{key}=\meta{value}'形式。

\switchcolumn[0]*
The argument includes a list of comma-separated \textsf{keyval}
options and has basic rules as follows:
\switchcolumn
参数包括一个由逗号分隔的\textsf{keyval}选项列表，并有以下基本规则：
\end{paracol}


\begin{itemize}\setlength{\itemsep}{-.5\parsep}
\columnratio{0.55}
\begin{paracol}{2}
\item Multiple lines are allowed, while blank lines are not.
\switchcolumn
\item 允许有多行，但不允许有空行。
\switchcolumn
\item Any spaces between words are ignored.
\switchcolumn\item 单词之间的空格会被忽略。
\switchcolumn
\item Options are basically order-independent.
(There are some exceptions. See Section~\ref{sec:optionorder} for details.)
\switchcolumn
\item 选项基本上是无序的。
（有一些例外情况，请参见第~\ref{sec:optionorder}节了解详细信息。）
\end{paracol}
\end{itemize}

\columnratio{0.55}
\begin{paracol}{2}
For example,
\begin{quote}
|\usepackage[a5paper,hmargin={3cm,.8in},height=10in]{geometry}|
\end{quote}
is equivalent to 
\begin{quote}
|\usepackage[height=10in,a5paper,hmargin={3cm,0.8in}]{geometry}|
\end{quote}
\switchcolumn
例如，
\begin{quote}
\begin{minted}{latex}
\usepackage[a5paper,hmargin={3cm,.8in},height=10in]{geometry}
\end{minted}
\end{quote}
等同于
\begin{quote}
\begin{minted}{latex}
\usepackage[height=10in,a5paper,hmargin={3cm,0.8in}]{geometry}
\end{minted}
\end{quote}


\switchcolumn[0]*
Some options are allowed to have sub-list, e.g. |{3cm,0.8in}|.
Note that the order of values in the sub-list is significant.
The above setting is also equivalent to the followings:
\begin{quote}
  |\usepackage{geometry}|\\
  |\geometry{height=10in,a5paper,hmargin={3cm,0.8in}}|
\end{quote}
or 
\begin{quote}
  |\usepackage[a5paper]{geometry}|\\
  |\geometry{hmargin={3cm,0.8in},height=8in}|\\
  |\geometry{height=10in}|.
\end{quote}
\switchcolumn
某些选项允许有子列表，例如 |{3cm,0.8in}|。
请注意，子列表中的值的顺序是重要的。
上述设置也等同于以下设置：
\begin{quote}
\begin{minted}{latex}
\usepackage{geometry}
\geometry{height=10in,a5paper,hmargin={3cm,0.8in}}
\end{minted}
\end{quote}
或者
\begin{quote}
\begin{minted}{latex}
\usepackage[a5paper]{geometry} 
\geometry{hmargin={3cm,0.8in},height=8in} 
\geometry{height=10in}.
\end{minted}
\end{quote}

\switchcolumn[0]*
Thus, multiple use of \cs{geometry} just appends options.
\switchcolumn
因此，多次使用 \cs{geometry} 只会追加选项。

\switchcolumn[0]*
\Gm\ supports package 
\textsl{calc}\footnote{CTAN:~\texttt{macros/latex/required/tools}}.
For example,
\begin{quote}
|\usepackage{calc}|\\
|\usepackage[textheight=20\baselineskip+10pt]{geometry}|
\end{quote}
\switchcolumn
\Gm\ 支持 \textsl{calc}\footnote{CTAN:~\texttt{macros/latex/required/tools}} 宏包。
例如，
\begin{quote}
\begin{minted}{latex}
\usepackage{calc}
\usepackage[textheight=20\baselineskip+10pt]{geometry}
\end{minted}
\end{quote}
\end{paracol}



\columnratio{0.55}
\begin{paracol}{2}
\subsection{Option types}
\Gm\ options are categorized into four types:
\switchcolumn
\subsection{选项类型}
\Gm\ 的选项被分为四种类型：
\end{paracol}


\begin{enumerate}\itemsep=0pt
\columnratio{0.55}
\begin{paracol}{2}
\item \textbf{Boolean type}
takes a boolean value (|true| or |false|). If no value,
|true| is set by default.
\begin{quote}
\meta{key}|=true|\OR|false|.\\
\meta{key} with no value is equivalent to 
\meta{key}|=true|.
\end{quote}
\textit{Examples:}~ |verbose=true|, |includehead|, 
|twoside=false|.\\
Paper name is the exception. The preferred paper name should be set
with no values. Whatever value is given, it is ignored. For
instance, |a4paper=XXX| is equivalent to |a4paper|.
\switchcolumn
\item \textbf{布尔类型}
可以取布尔值（|true| 或 |false|）。如果没有给出值，则默认为 |true|。
\begin{quote}
\meta{key}|=true|\OR|false|.\\
\meta{key} 没有给出值,等同于
\meta{key}|=true|.
\end{quote}

\textit{示例：}~ |verbose=true|, |includehead|,
|twoside=false|。\\
纸张名称是一个例外。应该使用没有值来设置首选纸张名称。无论给出什么值，都会被忽略。例如，|a4paper=XXX| 等同于 |a4paper|。

\switchcolumn[0]*
\item \textbf{Single-valued type}
takes a mandatory value.
\begin{quote}
\meta{key}|=|\meta{value}.
\end{quote}
\textit{Examples:}~ |width=7in|, |left=1.25in|,
|footskip=1cm|, |height=.86\paperheight|.
\switchcolumn
\item \textbf{单值类型}
必须给出一个值。
\begin{quote}
\meta{key}|=|\meta{value}.
\end{quote}
\textit{示例：}~ |width=7in|, |left=1.25in|,
|footskip=1cm|, |height=.86\paperheight|。

\switchcolumn[0]*
\item \textbf{Double-valued type}

takes a pair of comma-separated values in braces. The two values can
be shortened to one value if they are identical.
\begin{quote}
\meta{key}|=|\argii{value1}{value2}.\\
\meta{key}|=|\meta{value} is equivalent to 
\meta{key}|=|\argii{value}{value}
\end{quote}
\textit{Examples:}~ |hmargin={1.5in,1in}|, |scale=0.8|,
|body={7in,10in}|.
\switchcolumn

\item \textbf{双值类型}

需要用括号括起来的逗号分隔的一对值。如果两个值相同，可以缩写为一个值
\begin{quote}
\meta{key}|=|\argii{value1}{value2}.\\
\meta{key}|=|\meta{value} 等同于
\meta{key}|=|\argii{value}{value}
\end{quote}
\textit{示例：}~ |hmargin={1.5in,1in}|, |scale=0.8|,
|body={7in,10in}|。

\switchcolumn[0]*
\item \textbf{Triple-valued type}

takes three mandatory, comma-separated values in braces.
\begin{quote}
\meta{key}|=|\argiii{value1}{value2}{value3}
\end{quote}
Each value must be a dimension or null. When you give an empty value
or `|*|', it means null and leaves the appropriate value 
to the auto-completion mechanism. You need to specify at least one
dimension, typically two dimensions. You can set nulls for all the 
values, but it makes no sense.
\textit{Examples:}\\
\hspace*{2em} |hdivide={2cm,*,1cm}|, |vdivide={3cm,19cm, }|,
    |divide={1in,*,1in}|.
\switchcolumn
\item \textbf{三值类型}

需要给出三个必填的逗号分隔值。
\begin{quote}
\meta{key}|=|\argiii{value1}{value2}{value3}
\end{quote}
每个值必须是一个长度或空值。当给出空值或 `|*|' 时，表示为空值，并将相应的值留给自动补全机制。您需要至少指定一个长度，通常是两个长度。您可以为所有值设置为空值，但这没有意义。
\textit{示例：}\\
\hspace{2em} |hdivide={2cm,*,1cm}, vdivide={3cm,19cm, }, divide={1in,*,1in}|.
\end{paracol}
\end{enumerate}
