\columnratio{0.55}
\begin{paracol}{2}
 \subsection{Defaults}\label{sec:defaults}

 This section sums up the default settings for the auto-completion
 described later.
 
 The default vertical margin ratio is $2/3$, namely,
 \begin{equation}
  |top| : |bottom| = 2 : 3 \qquad\textit{default}.
 \end{equation}
\switchcolumn
\subsection{默认设置}

本节总结了后面描述的自动补全的默认设置。
 
默认的垂直边距比例是 $2/3$，即
 \begin{equation}
  |top| : |bottom| = 2 : 3 \qquad\textit{default}.
 \end{equation}

 \switchcolumn[0]*
 As for the horizontal margin ratio, the default value depends on
 whether the document is onesided or twosided,
 \begin{equation}
  |left|\;(|inner|) : |right|\;(|outer|) 
       = \left\{ \begin{array}{ll}
              1 : 1 \qquad\textit{default for oneside},\\
              2 : 3 \qquad\textit{default for twoside}.
         \end{array}\right.
 \end{equation}
\switchcolumn
至于水平边距比例，默认值取决于文档是单面还是双面的，
\begin{equation}
|left|\;(|inner|) : |right|\;(|outer|) 
    = \left\{ \begin{array}{ll}
            1 : 1 \qquad\textit{单面默认},\\
            2 : 3 \qquad\textit{双面默认}.
        \end{array}\right.
 \end{equation}

 \switchcolumn[0]*
 Obviously the default horizontal margin ratio for oneside is `centering'.

 The \Gm\ package has the following default setting for
 \textit{onesided} documents:

 \switchcolumn
 显然，单面的默认水平边距比例是“居中”。

 对于\Gm\ 宏包，默认的设置对于\textit{单面}文档如下：
\end{paracol}

\begin{itemize}\setlength{\itemsep}{-.5\parsep}
    \columnratio{0.55}
    \begin{paracol}{2}
\item |scale=0.7| (\gpart{body} is $0.7 \times \gpart{paper}$)
\switchcolumn\item |scale=0.7| （\gpart{正文}是 $0.7 \times \gpart{纸张}$）
\switchcolumn[0]*
\item |marginratio={1:1, 2:3}| (1:1 for horizontal and 2:3 for vertical margins)
\switchcolumn\item |marginratio={1:1, 2:3}| （水平边距比例为 1:1，垂直边距比例为 2:3）
\switchcolumn[0]*
\item |ignoreall| (the header, footer, marginal notes are excluded
when calculating the size of \gpart{body}.)
\switchcolumn\item |ignoreall| （在计算\gpart{正文}的大小时，头部、底部和边注都被排除在外。）
\end{paracol}
\end{itemize}

\columnratio{0.55}
\begin{paracol}{2}
 For \textit{twosided} document with |twoside| option, the default
 setting is the same as \textit{onesided} except that the horizontal
 margin ratio is set to |2:3| as well.

 Additional options overwrite the previous specified dimensions. 
\switchcolumn
对于带有 |twoside| 选项的\textit{双面}文档，默认设置与\textit{单面}相同，只是水平边距比例也设置为 |2:3|。

附加选项会覆盖先前指定的尺寸。
\end{paracol}