
\columnratio{0.55}
\begin{paracol}{2}
\subsection{Native dimensions}\label{sec:dimension}

The options below overwrite \LaTeX\ native dimensions and switches for page
layout (See the right-hand side in Figure~\ref{fig:layout}).
\switchcolumn
\subsection{原生尺寸}
下面的选项可以覆盖\LaTeX 的原生尺寸和页面布局开关（见图~\ref{fig:layout}的右侧）。
\end{paracol}

\begin{Options}
\columnratio{0.55}
\begin{paracol}{2}
\switchcolumn[0]*\item[headheight\OR head]~\\
   modifies \cs{headheight}, height of header.
   |headheight=|\meta{length} or |head=|\meta{length}.
\switchcolumn\item[headheight\OR head]~\\
修改\cs{headheight}，页眉的高度。
|headheight=|\meta{length} 或 |head=|\meta{length}。
\switchcolumn[0]*\item[headsep] modifies \cs{headsep}, separation between header and text
   (body). |headsep=|\meta{length}.
\switchcolumn
\item[headsep] 修改\cs{headsep}，页眉和正文（主体）之间的距离。
|headsep=|\meta{length}。
\switchcolumn[0]*\item[footskip\OR foot]~\\ modifies \cs{footskip}, distance separation
   between baseline of last line of text and baseline of footer.
   |footskip=|\meta{length} or |foot=|\meta{length}.
\switchcolumn\item[footskip\OR foot]~\\ 修改\cs{footskip}，正文最后一行的基线与页脚基线之间的距离。
|footskip=|\meta{length} 或 |foot=|\meta{length}。
\switchcolumn[0]*\item[nohead] eliminates spaces for the head of the page, which is
   equivalent to both \cs{headheight}|=0pt| and \cs{headsep}|=0pt|.
\switchcolumn\item[nohead] 消除页头的空白，等效于 \cs{headheight}|=0pt| 和 \cs{headsep}|=0pt|。
\switchcolumn[0]*\item[nofoot] eliminates spaces for the foot of the page, which is
   equivalent to \cs{footskip}|=0pt|.
\switchcolumn\item[nofoot] 消除页脚的空白，等效于 \cs{footskip}|=0pt|。
\switchcolumn[0]*\item[noheadfoot] equivalent to |nohead| and |nofoot|, which means that
   \cs{headheight}, \cs{headsep} and \cs{footskip} are all set to |0pt|.
\switchcolumn\item[noheadfoot] 等效于 |nohead| 和 |nofoot|，即将 \cs{headheight}、\cs{headsep} 和 \cs{footskip} 都设为 |0pt|。
\switchcolumn[0]*\item[footnotesep] changes the dimension \cs{skip}\cs{footins}, separation
   between the bottom of text body and the top of footnote text.
\switchcolumn\item[footnotesep] 修改 \cs{skip}\cs{footins} 的尺寸，即正文底部与脚注文本顶部之间的距离。
\switchcolumn[0]*\item[marginparwidth\OR marginpar]~\\ 
   modifies \cs{marginparwidth}, width of the marginal notes.
   |marginparwidth=|\meta{length}.
\switchcolumn\item[marginparwidth\OR marginpar]~\\
修改\cs{marginparwidth}，边注的宽度。
|marginparwidth=|\meta{length}。
\switchcolumn[0]*\item[marginparsep] modifies \cs{marginparsep}, separation between
   body and marginal notes. |marginparsep=|\meta{length}.
\switchcolumn\item[marginparsep] 修改\cs{marginparsep}，正文和边注之间的距离。
|marginparsep=|\meta{length}。
\switchcolumn[0]*\item[nomarginpar] shrinks spaces for marginal notes to 0pt, which
   is equivalent to \cs{marginparwidth}|=0pt| and \cs{marginparsep}|=0pt|.
\switchcolumn\item[nomarginpar] 将边注的空白缩小为0pt，等效于 \cs{marginparwidth}|=0pt| 和 \cs{marginparsep}|=0pt|。
\switchcolumn[0]*\item[columnsep] modifies \cs{columnsep}, the separation between two
   columns in |twocolumn| mode.
\switchcolumn\item[columnsep] 修改\cs{columnsep}，在双栏模式下两栏之间的距离。
\switchcolumn[0]*\item[hoffset]  modifies \cs{hoffset}. |hoffset=|\meta{length}.
\switchcolumn\item[hoffset] 修改\cs{hoffset}。 |hoffset=|\meta{length}。
\switchcolumn[0]*\item[voffset]  modifies \cs{voffset}. |voffset=|\meta{length}.
\switchcolumn\item[voffset] 修改\cs{voffset}。 |voffset=|\meta{length}。
\switchcolumn[0]*\item[offset] horizontal and vertical offset.\\
   |offset=|\argii{hoffset}{voffset} or |offset=|\meta{length}.
\switchcolumn\item[offset] 水平和垂直偏移。~\\
|offset=|\argii{hoffset}{voffset} 或 |offset=|\meta{length}。
\switchcolumn[0]*\item[twocolumn] sets |twocolumn| mode with \cs{@twocolumntrue}.
  |twocolumn=false| denotes onecolumn mode with\cs{@twocolumnfalse}.
  Instead of |twocolumn=false|, you can specify |onecolumn| (which
  defaults to |true|)
\switchcolumn\item[twocolumn] 使用 \cs{@twocolumntrue} 设置双栏模式。|twocolumn=false| 表示单栏模式，等效于 \cs{@twocolumnfalse}。你也可以使用 |onecolumn| 来代替 |twocolumn=false|（默认为 |true|）。
\switchcolumn[0]*\item[onecolumn] works as |twocolumn=false|. On the other hand,
  |onecolumn=false| is equivalent to |twocolumn|. 
\switchcolumn\item[onecolumn] 等效于 |twocolumn=false|。另一方面，|onecolumn=false| 等效于 |twocolumn|。
\switchcolumn[0]*\item[twoside] sets both \cs{@twosidetrue} and \cs{@mparswitchtrue}.
  See Section~\ref{sec:margin}.
\switchcolumn\item[twoside] 同时设置 \cs{@twosidetrue} 和 \cs{@mparswitchtrue}。见第~\\ref{sec:margin}节。
\switchcolumn[0]*\item[textwidth] sets \cs{textwidth} directly. See Section~\ref{sec:body}.
\switchcolumn\item[textwidth] 直接设置 \cs{textwidth}。见第\ref{sec:body}节。
\switchcolumn[0]*\item[textheight] sets \cs{textheight} directly. See Section~\ref{sec:body}.
\switchcolumn\item[textheight] 直接设置 \cs{textheight}。见第~\\ref{sec:body}节。
\switchcolumn[0]*\item[reversemp\OR reversemarginpar]~\\
  makes the marginal notes appear in the left (inner) margin with
  \cs{@reversemargintrue}. The option doesn't change |includemp| mode.
  It's set |false| by default.
  \switchcolumn\item[reversemp\OR reversemarginpar]~\\ 这个选项使用 \cs{@reversemargintrue} 让边注出现在左侧（内侧）边距。这个选项不会改变 |includemp| 模式。默认情况下，该选项为 |false|。
\end{paracol}
\end{Options}
