\columnratio{0.55}
\begin{paracol}{2}
\subsection{Order of options}\label{sec:optionorder}

The specification of \Gm\ options is order-independent,
and overwrites the previous one for the same setting.
For example, 
\switchcolumn
\subsection{选项的顺序}

\Gm\ 选项的指定是无序的，并且会覆盖先前相同设置的选项。
例如，

\switchcolumn[0]*
\begin{center}
|[left=2cm, right=3cm]| is equivalent to 
|[right=3cm, left=2cm]|.
\end{center}
\switchcolumn
\begin{center}
|[left=2cm, right=3cm]| 等同于
|[right=3cm, left=2cm]|.
\end{center}

\switchcolumn[0]*
 The options called multiple times overwrite the previous
 settings. For example, 
 \begin{center}
  |[verbose=true, verbose=false]| results in |verbose=false|. 
 \end{center}
 |[hmargin={3cm,2cm}, left=1cm]| is the same as |hmargin={1cm,2cm}|, 
where the left (or inner) margin is overwritten by |left=1cm|. 
\switchcolumn
多次调用的选项会覆盖先前的设置。例如，
\begin{center}
|[verbose=true, verbose=false]| 的结果是 |verbose=false|。
\end{center}
|[hmargin={3cm,2cm}, left=1cm]| 等同于 |hmargin={1cm,2cm}|，其中左侧（或内侧）边距被 |left=1cm| 覆盖。        

\switchcolumn[0]*
 |reset| and |mag| are exceptions.
 The |reset| option removes all the geometry options (except |pass|)
 before it. If you set
 \begin{quote}
 |\documentclass[landscape]{article}|\\
 |\usepackage[margin=1cm,twoside]{geometry}|\\
 |\geometry{a5paper, reset, left=2cm}|
 \end{quote}
\switchcolumn
|reset| 和 |mag| 是例外。
|reset| 选项会在其之前删除所有的几何选项（除了 |pass|）。如果您设置
\begin{quote}
|\documentclass[landscape]{article}|\\
|\usepackage[margin=1cm,twoside]{geometry}|\\
|\geometry{a5paper, reset, left=2cm}|
\end{quote}

\switchcolumn[0]*
 then |margin=1cm|, |twoside| and |a5paper| are removed, and 
 is eventually equivalent to
 \begin{quote}
 |\documentclass[landscape]{article}|\\
 |\usepackage[left=2cm]{geometry}|
 \end{quote}
 \switchcolumn
 那么 |margin=1cm|、|twoside| 和 |a5paper| 被删除，并最终等同于
\begin{quote}
|\documentclass[landscape]{article}|\\
|\usepackage[left=2cm]{geometry}|
\end{quote}
\switchcolumn[0]*
 The |mag| option should be set in advance of any other settings with
 `true' length, such as |left=1.5truecm|, |width=5truein| and so on.
 The |\mag| primitive can be set before this package is called.
\switchcolumn
|mag| 选项应该在任何其他带有 `true' 长度的设置之前进行设置，例如 |left=1.5truecm|、|width=5truein| 等等。
|\mag| 原语可以在调用此宏包之前进行设置。

\end{paracol}
