\begin{optionlist}
\columnratio{0.55}
\begin{paracol}{2}
\switchcolumn[0]*%%%%%%%%%%%%
\item[mathescape (boolean) (false)]
Enable \LaTeX{} math mode inside comments.
Usage as in package \pkg{listings}.
See the note under \texttt{escapeinside} regarding math and ligatures.
\switchcolumn
\item[mathescape (布尔值) (false)]
在注释中启用\LaTeX{}数学模式。与\pkg{listings}包中的用法相同。请参阅有关数学和连字符的注释的说明。
\switchcolumn[0]*%%%%%%%%%%%%
\item[texcl (boolean) (false)]
Enables \LaTeX{} code inside comments.
Usage as in package \pkg{listings}.  See the note under \texttt{escapeinside} regarding math and ligatures.
\switchcolumn
\item[texcl (布尔值) (false)]
在注释中启用\LaTeX{}代码。与\pkg{listings}包中的用法相同。请参阅有关数学和连字符的注释的说明。
\switchcolumn[0]*%%%%%%%%%%%%
\item[texcomments (boolean) (false)]
Enables \LaTeX{} code inside comments.  The newer name for |texcl|.  See the note under |escapeinside| regarding math and ligatures.
\switchcolumn
\item[texcomments (布尔值) (false)]
在注释中启用\LaTeX{}代码。这是|texcl|的新名称。有关数学和连字符的注释的注意事项，请参见|escapeinside|。
\switchcolumn[0]*%%%%%%%%%%%%
As of Pygments 2.0.2, \texttt{texcomments} fails with multiline C/C++ preprocessor directives, and may fail in some other circumstances.  This is because preprocessor directives are \href{http://pygments.org/docs/tokens/}{tokenized as \texttt{Comment.Preproc}}, so \texttt{texcomments} causes preprocessor directives to be treated as literal \LaTeX\ code.  \href{https://bitbucket.org/birkenfeld/pygments-main/issue/1086/wrong-processing-of-in-c-c-macros-if-is}{An issue has been opened} at the Pygments site; additional details are also available on the \href{https://github.com/gpoore/minted/issues/66}{\pkg{minted} GitHub site}.
\switchcolumn
从Pygments 2.0.2开始，\texttt{texcomments}在多行C/C++预处理器指令中失败，并且在某些其他情况下可能会失败。这是因为预处理器指令被\href{http://pygments.org/docs/tokens/}{令牌化为\texttt{Comment.Preproc}}，因此\texttt{texcomments}会导致将预处理器指令视为字面\LaTeX{}代码。在Pygments站点上已经打开了一个\href{https://bitbucket.org/birkenfeld/pygments-main/issue/1086/wrong-processing-of-in-c-c-macros-if-is}{问题}；关于此问题还可以在\href{https://github.com/gpoore/minted/issues/66}{\pkg{minted} GitHub站点}上找到其他详细信息。
\end{paracol}
\end{optionlist}
