\begin{optionlist}
\columnratio{0.55}
\begin{paracol}{2}
\switchcolumn[0]*%%%%%%%%%%%%
\item[breakbefore (string) (\meta{none})]
Break lines before specified characters, not just at spaces, when \texttt{breaklines=true}.  Does not apply to |\mintinline|.
\switchcolumn
\item[breakbefore (字符串) (\meta{none})]
在指定的字符之前换行，而不仅仅是在空格处换行，当\texttt{breaklines=true}时。不适用于|\mintinline|。
\switchcolumn[0]*%%%%%%%%%%%%
For example, \texttt{breakbefore=A} would allow breaks before capital A's.  Special characters given to \texttt{breakbefore} should be backslash-escaped (usually \texttt{\hashchar}, \texttt{\{}, \texttt{\}}, \texttt{\%}, \texttt{[}, \texttt{]}; the backslash \texttt{\textbackslash} may be obtained via \texttt{\textbackslash\textbackslash}).
\switchcolumn
例如，\texttt{breakbefore=A}允许在大写A之前断行。\texttt{breakbefore}所给出的特殊字符应该以反斜杠转义（通常为\texttt{\hashchar}, \texttt{\{}, \texttt{\}}, \texttt{\%}, \texttt{[}, \texttt{]}; 反斜杠 \texttt{\textbackslash} 可以通过 \texttt{\textbackslash\textbackslash} 获得。
\switchcolumn[0]*%%%%%%%%%%%%
 For an alternative, see \texttt{breakafter}.  When \texttt{breakbefore} and \texttt{breakafter} are used for the same character, \texttt{breakbeforegroup} and \texttt{breakaftergroup} must both have the same setting.
 \switchcolumn
对于另一种选择，请参见\texttt{breakafter}。当\texttt{breakbefore}和\texttt{breakafter}同时用于同一个字符时，\texttt{breakbeforegroup}和\texttt{breakaftergroup}必须具有相同的设置。
\switchcolumn[0]*%%%%%%%%%%%%
\begin{longexample}
    \begin{minted}[breaklines, breakbefore=A]{python}
    some_string = 'SomeTextThatGoesOnAndOnForSoLongThatItCouldNeverFitOnOneLine'
    \end{minted}
\end{longexample}
\switchcolumn
\begin{longexample}
    \begin{minted}[breaklines, breakbefore=A]{python}
    some_string = 'SomeTextThatGoesOnAndOnForSoLongThatItCouldNeverFitOnOneLine'
    \end{minted}
\end{longexample}
\switchcolumn[0]*%%%%%%%%%%%%
  \item[breakbeforegroup] (boolean) (true)
    When \texttt{breakbefore} is used, group all adjacent identical characters together, 
    and only allow a break before the first character.  When \texttt{breakbefore} and 
    \texttt{breakafter} are used for the same character, \texttt{breakbeforegroup} and 
    \texttt{breakaftergroup} must both have the same setting.
    \switchcolumn
    \item[breakbeforegroup] (布尔值) (true)
    当使用\texttt{breakbefore}时，将所有相邻的相同字符分组在一起，并且只允许在第一个字符之前断行。当\texttt{breakbefore}和\texttt{breakafter}同时用于同一个字符时，\texttt{breakbeforegroup}和\texttt{breakaftergroup}必须具有相同的设置。
\switchcolumn[0]*%%%%%%%%%%%%
  \item[breakbeforesymbolpre (string) (\string\,\string\footnotesize\string\ensuremath\{\_\string\rfloor\}, \,\footnotesize\ensuremath{_\rfloor})]
    The symbol inserted pre-break for breaks inserted by \texttt{breakbefore}.
    \switchcolumn
    \item[breakbeforesymbolpre (字符串) (\string\,\string\footnotesize\string\ensuremath\{\_\string\rfloor\}, \,\footnotesize\ensuremath{_\rfloor})]
    在\texttt{breakbefore}插入的断行符号之前插入的符号。
    \switchcolumn[0]*%%%%%%%%%%%%
  \item[breakbeforesymbolpost (string) (\meta{none})]
    The symbol inserted post-break for breaks inserted by \texttt{breakbefore}.
    \switchcolumn
    \item[breakbeforesymbolpost (字符串) (\meta{none})]
    在\texttt{breakbefore}插入的断行符号之后插入的符号。
\end{paracol}
\end{optionlist}
