\begin{optionlist}
\columnratio{0.55}
\begin{paracol}{2}
\switchcolumn[0]*%%%%%%%%%%%%
\item[breakautoindent (boolean) (true)]
When a line is broken, automatically indent the continuation lines to the indentation level of the first line.  When \texttt{breakautoindent} and \texttt{breakindent} are used together, the indentations add.  This  indentation is combined with \texttt{breaksymbolindentleft} to give the total actual left indentation.  Does not apply to \texttt{\string\mintinline}.
\switchcolumn
\item[breakautoindent (布尔值) (true)]
当换行时，自动将续行缩进到第一行的缩进级别。当\texttt{breakautoindent}和\texttt{breakindent}一起使用时，缩进级别会相加。此缩进与\texttt{breaksymbolindentleft}结合在一起，形成实际的左缩进总量。不适用于\texttt{\string\mintinline}。

\switchcolumn[0]*%%%%%%%%%%%%
\item[breakindent (dimension) (\meta{breakindentnchars})]
When a line is broken, indent the continuation lines by this amount.  When |breakautoindent| and |breakindent| are used together, the indentations add.  This  indentation is combined with |breaksymbolindentleft| to give the total actual left indentation.
\switchcolumn
\item[breakindent (尺寸) (\meta{breakindentnchars})]
当一行被断行时，将连续行缩进这个量。当|breakautoindent|和|breakindent|一起使用时，缩进会相加。此缩进与|breaksymbolindentleft|相结合，给出总的实际左缩进。
\switchcolumn[0]*%%%%%%%%%%%%
Does not apply to \texttt{\string\mintinline}.
\switchcolumn
不适用于\texttt{\string\mintinline}。
\switchcolumn[0]*%%%%%%%%%%%%
\item[breakindentnchars (integer) (0)]
This allows |breakindent| to be specified as an integer number of characters rather than as a dimension (assumes a fixed-width font).
\switchcolumn
\item[breakindentnchars (整数) (0)]
这允许将|breakindent|指定为整数个字符而不是作为尺寸（假设使用等宽字体）。

\end{paracol}
\end{optionlist}
