\columnratio{0.55}
\begin{paracol}{2}
\section{Installation} 
\switchcolumn
\section{安装}
\switchcolumn[0]*%%%%%%%%%
\subsection{Prerequisites}
\switchcolumn
\subsection{先决条件}
\switchcolumn[0]*%%%%%%%%%
\app{Pygments} is written in Python, so make sure that you have Python 2.6 or later installed on your system.  This may be easily checked from the command line:
\begin{Verbatim}[gobble=3,commandchars=\\\{\}]
   \$ python --version
   Python 2.7.5
\end{Verbatim}
\switchcolumn
\app{Pygments} 是用 Python 编写的，所以请确保您的系统上已安装 Python 2.6 或更高版本。您可以通过命令行轻松检查：
\begin{Verbatim}[gobble=0,commandchars=\\\{\}]
\$ python --version
Python 2.7.5
\end{Verbatim}
\switchcolumn[0]*%%%%%%%%%
If you don't have Python installed, you can download it from the \href{http://www.python.org/download/}{Python website} or
use your operating system's package manager.
\switchcolumn
如果您尚未安装 Python，可以从\href{http://www.python.org/download/}{Python网站}下载，或使用您操作系统的软件包管理器。
\switchcolumn[0]*%%%%%%%%%
Some Python distributions include \pkg{Pygments} (see some of the options under ``Alternative Implementations'' on the Python site).  Otherwise, you will need to install \pkg{Pygments} manually. This may  be done by installing \href{http://pypi.python.org/pypi/setuptools}{\app{setuptools}}, which facilitates the distribution of Python applications.  You can then install \app{Pygments} using the following command:
\switchcolumn
某些 Python 发行版已经包含了 \pkg{Pygments}（请参考 Python 网站上的“替代实现”选项）。否则，您需要手动安装 \pkg{Pygments}。可以通过安装\href{http://pypi.python.org/pypi/setuptools}{\app{setuptools}}来完成，它可以方便地分发 Python 应用程序。然后，您可以使用以下命令安装 \app{Pygments}：
\switchcolumn[0]*%%%%%%%%%
\begin{Verbatim}[commandchars=\\\{\}]
\$ sudo easy_install Pygments
\end{Verbatim}
\switchcolumn
\begin{Verbatim}[commandchars=\\\{\}]
\$ sudo easy_install Pygments
\end{Verbatim}
\switchcolumn[0]*%%%%%%%%%
Under Windows, you will not need the |sudo|, but may need to run the command prompt as administrator.  \pkg{Pygments} may also be installed with |pip|:
\begin{Verbatim}[commandchars=\\\{\}]
\$ pip install Pygments
\end{Verbatim}
\switchcolumn
在 Windows 下，您不需要使用 |sudo|，但可能需要以管理员身份运行命令提示符。也可以使用 |pip|\footnote{译注：最新的使用pip3安装，2版本的安装不了了！} 安装 \pkg{Pygments}：
\begin{Verbatim}[commandchars=\\\{\}]
\$ pip install Pygments
\end{Verbatim}
\switchcolumn[0]*%%%%%%%%%
If you already have \app{Pygments} installed, be aware that the latest version is recommended (at least 1.4 or later).  Some features, such as |escapeinside|, will only work with 2.0+.  \pkg{minted} may work with versions as early as 1.2, but there are no guarantees.
\switchcolumn
如果您已经安装了 \app{Pygments}，请注意建议使用最新版本（至少为 1.4 或更高版本）。某些功能，如 |escapeinside|，只能在 2.0+ 版本中工作。\pkg{minted} 可能与早期版本（至少为 1.2）一起工作，但不能保证。
\switchcolumn[0]*%%%%%%%%%
\subsection{Required packages}
\switchcolumn
\subsection{所需软件包}
\switchcolumn[0]*%%%%%%%%%
\pkg{minted} requires that the following packages be available and reasonably up to date on your system.  All of these ship with recent \TeX\ distributions.
\switchcolumn
\pkg{minted} 需要以下软件包在您的系统上可用且相对较新。这些软件包都包含在最新的 \TeX\ 发行版中。
\end{paracol}
\begin{multicols}{6}
\begingroup
\setlength\parskip{0pt}
\setlength\topsep{0pt}
\begin{list}{\textrm{\labelitemi}}{\ttfamily}
  \item keyval
  \item kvoptions
  \item fancyvrb
  \item fvextra
  \item upquote
  \item float
  \item ifthen
  \item calc
  \item ifplatform
  \item pdftexcmds
  \item etoolbox
  \item xstring
  \item xcolor
  \item lineno
  \item framed
  \item shellesc\footnote{for luatex 0.87+}
  \item catchfile
\end{list}
\endgroup
\end{multicols}

\columnratio{0.55}
\begin{paracol}{2}
\switchcolumn[0]*%%%%%%%%%
\subsection{Installing \pkg{minted}}
\label{sec:installing:installing}
\switchcolumn
\subsection{安装 \pkg{minted}}
\switchcolumn[0]*%%%%%%%%%
You can probably install \pkg{minted} with your \TeX\ distribution's package manager.  Otherwise, or if you want the absolute latest version, you can install it manually by following the directions below.
\switchcolumn
您可以使用 \TeX\ 发行版的软件包管理器安装 \pkg{minted}。否则，如果您想要安装最新版本，可以按照以下说明手动安装。
\switchcolumn[0]*%%%%%%%%%
You may download |minted.sty| from the
\href{https://github.com/gpoore/minted}{project's homepage}.  We have to install the file so that \TeX\ is able to find it.
In order to do that, please refer to the
\href{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=inst-wlcf}{\TeX{} FAQ}.
If you just want to experiment with the latest version, you could locate your current |minted.sty| in your \TeX\ installation and replace it with the latest version.  Or you could just put the latest |minted.sty| in the same directory as the file you wish to use it with.
\switchcolumn
您可以从\href{https://github.com/gpoore/minted}{项目主页}下载 |minted.sty|。我们需要将该文件安装到使 \TeX\ 能够找到它的位置。
为此，请参考\href{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=inst-wlcf}{\TeX{} FAQ}。
如果您只是想尝试最新版本，可以找到您当前 \TeX\ 安装中的 |minted.sty|，并将其替换为最新版本。或者，您可以将最新的 |minted.sty| 放在与要使用它的文件相同的目录中。
\end{paracol}