\chapter{Introducing PDF and iText}

\begin{itemizeSum}
    \item  A summary of what will be presented in this book\\本书将介绍的概述

    \item  Compiling and executing your first example\\编译和执行您的第一个示例
    
    \item  Learning the five steps in iText’s PDF creation process\\学习iText PDF创建过程中的五个步骤
\end{itemizeSum}


Call me Bruno. About ten years ago—never mind how long precisely—I thought I’d create a small PDF library in Java and publish it as free and open source software (F/OSS). Little did I know that this would lead to my writing a whale of a book about the extensive functionality that has been added over the years.

请叫我布鲁诺。大约十年前——不用管确切的时间——我想创建一个小的Java PDF库，并将其发布为自由和开源软件（F/OSS）。我万万没想到，这会导致我写一本关于多年来添加的广泛功能的大书。

That library was iText, and the book was titled iText in Action: Creating and Manipulating PDF (2007). Today, iText is the world’s leading F/OSS PDF library. It’s released under the Affero General Public License (AGPL) and is available in two versions: the original Java version, and the C\# port, iTextSharp. These libraries make it possible for you to enhance applications with dynamic PDF solutions. You can use iText to create invoices for your customers if you have a web shop, to produce tickets if you work for an airline or railway company, and so on. You can integrate iText into an application to generate PDF documents as an alternative to 
printing on paper, to add digital signatures to a document, to split or concatenate different documents, and so forth.

那个库就是iText，而那本书的标题是《iText in Action：创建和操作PDF》（2007年）。如今，iText是世界领先的F/OSS PDF库。它在Affero通用公共许可证（AGPL）下发布，并提供两个版本：原始的Java版本和C\#端口iTextSharp。这些库使您可以使用动态PDF解决方案增强应用程序。如果您有一个网店，您可以使用iText为客户创建发票，如果您在航空或铁路公司工作，则可以生成机票等。您可以将iText集成到应用程序中，以生成PDF文档作为替代纸张打印，在文档中添加数字签名，拆分或连接不同的文档等。

In the first edition of iText in Action, readers learned why things work the way they do in iText, complemented with simple examples. This second edition takes you further with more real-life examples, skipping a bit on the whys, but presenting comprehensive code samples that you can use to solve everyday problems.

在《iText in Action》的第一版中，读者了解了为什么iText的工作方式，辅以简单的示例。这本第二版将通过更多的实际示例带您走得更远，跳过一些原理，但提供全面的代码示例，您可以使用它们来解决日常问题。

In this chapter, I’ll give you a quick overview of the things you can do with PDF—
you’ll compile and execute a first “Hello World” example—and you’ll learn the basics of creating PDFs with iText.

在本章中，我将为您快速概述可以使用PDF做什么——您将编译并执行第一个“Hello World”示例，并学习使用iText创建PDF的基础知识。