\begin{docKeys}[
    doc no index,   %  no index entries for this example
    doc parameter = {~},
    ]
    {
    {
        doc name        = --list,
        doc description = 完整形式,
    },
    {
        doc name        = -l,
        doc description = 缩写形式,
    },
    }
    
List user level command sequences of the given packages (L).

列出给定包的用户级别命令序列 (L)。
    
\begin{tcblisting}{%title={Snapshot of the staging area},
csh texdef result={
\mintinline[breaklines]{shell}|latexdef --tempdir /Volumes/RamDisk -p xspace -l|
}
}
Defined by file 'xspace.sty':
\CurrentFile
\CurrentFilePath
\CurrentFilePathUsed
\CurrentFileUsed
\__hook_clist_gput:NV
\__hook_tl_gput:Nn
\__prop_map_0:wn
\__prop_map_1:wn
\__prop_pair:wn
\__prop_split_aux:w
\__seq_item:n
\__seq_map_1:w
\g__hook_file/after_labels_clist
\l__clist_internal_clist
\l__hook_cur_hook_tl
\l__hook_front_tl
\l__hook_label_0_tl
\l__hook_label_filehook-2020_seq
\l__hook_label_filehook-2020_tl
\l__hook_labels_seq
\l__hook_rear_tl
\l__hook_return_tl
\l__hook_work_prop
\protect
\xspace
\xspaceaddexceptions
\xspaceremoveexception
\end{tcblisting}

% \begin{commandshell} 
% latexdef -c '[a4paper]{book}' -v paperwidth
% latexdef -c '[letter]{book}'  -v paperwidth
% \end{commandshell}  
\end{docKeys}
    
    

\begin{docKeys}[
    doc no index,   %  no index entries for this example
    doc parameter = {~},
    ]
    {
    {
        doc name        = --list-defs,
        doc description = 完整形式,
    },
    {
        doc name        = -L,
        doc description = 缩写形式,
    },
}

List user level command sequences and their shorten definitions of the given packages (L).

列出给定包的用户级别命令序列及其简短定义 (L)。
     
\begin{tcblisting}{%title={Snapshot of the staging area},
csh texdef result={
\mintinline[breaklines]{shell}|latexdef --tempdir /Volumes/RamDisk -p xspace -L|
}
}
Defined by file 'xspace.sty':
\CurrentFile: macro:->xspace.sty
\CurrentFilePath: macro:->
\CurrentFilePathUsed: macro:->
\CurrentFileUsed: macro:->xspace.sty
\__hook_clist_gput:NV: \protected\long macro:->\exp_args:NNV \clist_gput_l
\__hook_tl_gput:Nn: \protected\long macro:#1#2->\__hook_tl_gset:Nx #1{\__k
\__prop_map_0:wn: \long macro:#1\s__prop #2->\msg_expandable_error:nn \ETC
\__prop_map_1:wn: \protected\long macro:#1\s__prop #2->\prop_map_inline:Nn
\__prop_pair:wn: \long macro:#1\s__prop #2->\msg_expandable_error:nn \ETC.
\__prop_split_aux:w: \long macro:#1\__prop_pair:wn filehook-2020\s__prop \
\__seq_item:n: \long macro:->\msg_expandable_error:nn {seq}\ETC.
\__seq_map_1:w: \long macro:->\msg_expandable_error:nn {seq}\ETC.
\g__hook_file/after_labels_clist: macro:->filehook-2020
\l__clist_internal_clist: macro:->filehook-2020
\l__hook_cur_hook_tl: macro:->file/after
\l__hook_front_tl: macro:->0
\l__hook_label_0_tl: macro:->filehook-2020
\l__hook_label_filehook-2020_seq: macro:->\s__seq 
\l__hook_label_filehook-2020_tl: macro:->0
\l__hook_labels_seq: macro:->\s__seq \__seq_item:n {filehoo\ETC.
\l__hook_rear_tl: macro:->filehook-2020
\l__hook_return_tl: macro:->\filehook@set@CurrentFile \filehook@atend \ETC
\l__hook_work_prop: macro:->\s__prop \__prop_pair:wn fileh\ETC.
\protect: \string
\xspace: macro:->\protect \xspace  
\xspaceaddexceptions: macro:->\g@addto@macro \@xspace@exceptions@tlp 
\xspaceremoveexception: macro:#1->\def \reserved@a ##1#1##2##3\ETC.
\end{tcblisting}
\end{docKeys}

\begin{docKeys}[
    doc no index,   %  no index entries for this example
    doc parameter = {~},
    ]
    {
    {
        doc name        = --list-all,
        doc description = 完整形式,
    },
    {
        doc name        = -ll,
        doc description = 缩写形式,
    },
}

List all command sequences of the given packages (L).

列出给定包的所有命令序列 (L)。
     
% \begin{commandshell} 
% latexdef -c '[a4paper]{book}' -v paperwidth
% latexdef -c '[letter]{book}'  -v paperwidth
% \end{commandshell}  
\end{docKeys}


\begin{docKeys}[
    doc no index,   %  no index entries for this example
    doc parameter = {~},
    ]
    {
    {
        doc name        = --list-defs-all,
        doc description = 完整形式,
    },
    {
        doc name        = -LL,
        doc description = 缩写形式,
    },
} 

List all command sequences and their shorten definitions of the given packages (L).

列出给定包的所有命令序列及其简短定义 (L)。
     
% \begin{commandshell} 
% latexdef -c '[a4paper]{book}' -v paperwidth
% latexdef -c '[letter]{book}'  -v paperwidth
% \end{commandshell}  
\end{docKeys}
    