
 %\clearpage
\begin{docTcbKey}[][doc new={2017-06-28}]{inherit height}{\colOpt{=\meta{fraction}}}{default |1|, initially unset}
If this option is used for a |tcolorbox| which is embedded inside
another (outer) |tcolorbox| \emph{and} if this outer |tcolorbox| has
a fixed height, then the given \meta{fraction} of the available text height
of the outer |tcolorbox| is used as \refKeyLe{/tcb/height} for the current
|tcolorbox|.
Otherwise, \refKeyLe{/tcb/natural height} is applied for the current
|tcolorbox|.

如果此项所设置的 |tcolorbox| 是个嵌入在另一个%(外部)
|tcolorbox| 中，\emph{且}外部分的这个 |tcolorbox| 有着固定的高度, 那么，设定的 \meta{fraction} 乘以外部的这个 |tcolorbox| 盒子的剩余高度用作当前盒子的高度 \refKeyLe{/tcb/height}。否则，当前 |tcolorbox| 盒子将应用自然高度 \refKeyLe{/tcb/natural height} 。

\begin{exdispExample}{inherit_height}
\tcbset{colframe=blue!75!black,colback=white,fonttitle=\bfseries}

\begin{tcolorbox}[title=外部盒子指定高度为4cm,height=4cm]
\begin{tcolorbox}[title=Inner box,nobeforeafter,inherit height]
这个内部盒子的高度使用外盒的剩余高度空间。
\end{tcolorbox}
\end{tcolorbox}

\begin{tcolorbox}[title=外部盒子使用自然高度]
\begin{tcolorbox}[title=Inner box,nobeforeafter,inherit height]
这个盒子使用自身的自然高度。
\end{tcolorbox}
\end{tcolorbox}

Deeply nested box using 60 percent of the available space.
Deeply nested box using 40 percent of the available space.
\begin{tcolorbox}[title=外部盒子指定高度为5cm,height=5cm]
\begin{tcolorbox}[title=内部盒子,nobeforeafter,inherit height]
\begin{tcolorbox}[colframe=red,beforeafter skip=0pt,inherit height=0.6]
\verb|inherit height=0.6|    使用60\%可用空间的嵌套盒子。
\end{tcolorbox}
\begin{tcolorbox}[colframe=red,beforeafter skip=0pt,inherit height=0.4]
\verb|inherit height=0.4|    使用40\%可用空间的嵌套盒子。
\end{tcolorbox}
\end{tcolorbox}
\end{tcolorbox}
\end{exdispExample}
\end{docTcbKey}