\columnratio{0.55}
\begin{paracol}{2}
\switchcolumn[0]*%%%%%%%
\section{Quick Start}
\switchcolumn
\section{快速上手}
\switchcolumn[0]*%%%%%%%
\subsection{Try Vue Online}
\switchcolumn
\subsection{线上尝试 Vue}
\switchcolumn[0]*%%%%%%%
\begin{itemize}
\item
    To quickly get a taste of Vue, you can try it directly in our
    \href{https://play.vuejs.org/\#eNo9jcEKwjAMhl/lt5fpQYfXUQfefAMvvRQbddC1pUuHUPrudg4HIcmXjyRZXEM4zYlEJ+T0iEPgXjn6BB8Zhp46WUZWDjCa9f6w9kAkTtH9CRinV4fmRtZ63H20Ztesqiylphqy3R5UYBqD1UyVAPk+9zkvV1CKbCv9poMLiTEfR2/IXpSoXomqZLtti/IFwVtA9A==}{Playground}.
\item
    If you prefer a plain HTML setup without any build steps, you can use
    this \href{https://jsfiddle.net/yyx990803/2ke1ab0z/}{JSFiddle} as your
    starting point.
\item
    If you are already familiar with Node.js and the concept of build
    tools, you can also try a complete build setup right within your
    browser on \href{https://vite.new/vue}{StackBlitz}.
\end{itemize}
\switchcolumn
\begin{itemize}
\item
    想要快速体验
    Vue，你可以直接试试我们的\href{https://play.vuejs.org/\#eNo9jcEKwjAMhl/lt5fpQYfXUQfefAMvvRQbddC1pUuHUPrudg4HIcmXjyRZXEM4zYlEJ+T0iEPgXjn6BB8Zhp46WUZWDjCa9f6w9kAkTtH9CRinV4fmRtZ63H20Ztesqiylphqy3R5UYBqD1UyVAPk+9zkvV1CKbCv9poMLiTEfR2/IXpSoXomqZLtti/IFwVtA9A==}{演练场}。
\item
    如果你更喜欢不用任何构建的原始 HTML，可以使用
    \href{https://jsfiddle.net/yyx990803/2ke1ab0z/}{JSFiddle} 入门。
\item
    如果你已经比较熟悉 Node.js 和构建工具等概念，还可以直接在浏览器中打开
    \href{https://vite.new/vue}{StackBlitz} 来尝试完整的构建设置。
\end{itemize}
\switchcolumn[0]*%%%%%%%
\subsection{Creating a Vue Application}
\switchcolumn
\subsection{创建一个 Vue 应用}
\switchcolumn[0]*%%%%%%%
\begin{vueQuote}{Prerequisites}
\begin{itemize}
\item
    Familiarity with the command line
\item
    Install \href{https://nodejs.org/}{Node.js} version 16.0 or higher
\end{itemize}        
\end{vueQuote}    
\switchcolumn
\begin{vueQuote}{前提条件}
\begin{itemize}
\item
    熟悉命令行
\item
    已安装 16.0 或更高版本的 \href{https://nodejs.org/}{Node.js}
\end{itemize}
\end{vueQuote}    
\switchcolumn[0]*%%%%%%%
In this section we will introduce how to scaffold a Vue
\href{https://vuejs.org/guide/extras/ways-of-using-vue.html\#single-page-application-spa}{Single
Page Application} on your local machine. The created project will be
using a build setup based on \href{https://vitejs.dev/}{Vite} and allow
us to use Vue
\href{https://vuejs.org/guide/scaling-up/sfc.html}{Single-File
Components} (SFCs).
\switchcolumn
在本节中，我们将介绍如何在本地搭建 Vue
\href{https://cn.vuejs.org/guide/extras/ways-of-using-vue.html\#single-page-application-spa}{单页应用}。创建的项目将使用基于
\href{https://vitejs.dev/}{Vite} 的构建设置，并允许我们使用 Vue
的\href{https://cn.vuejs.org/guide/scaling-up/sfc.html}{单文件组件}
(SFC)。
\switchcolumn[0]*%%%%%%%
Make sure you have an up-to-date version of
\href{https://nodejs.org/}{Node.js} installed and your current working
directory is the one where you intend to create a project. Run the
following command in your command line (without the
\texttt{\textgreater{}} sign): 
\switchcolumn
确保你安装了最新版本的
\href{https://nodejs.org/}{Node.js}，并且你的当前工作目录正是打算创建项目的目录。在命令行中运行以下命令
(不要带上 \texttt{\textgreater{}} 符号)：
\switchcolumn[0]*%%%%%%%
\begin{codeShell}
npm create vue@latest
\end{codeShell}
\switchcolumn
\begin{codeShell}
npm create vue@latest
\end{codeShell}
\switchcolumn[0]*%%%%%%%
This command will install and execute
\href{https://github.com/vuejs/create-vue}{create-vue}, the official Vue
project scaffolding tool. You will be presented with prompts for several
optional features such as TypeScript and testing support:
\switchcolumn
这一指令将会安装并执行
\href{https://github.com/vuejs/create-vue}{create-vue}，它是 Vue
官方的项目脚手架工具。你将会看到一些诸如 TypeScript
和测试支持之类的可选功能提示：
\switchcolumn[0]*%%%%%%%
\begin{codeConsole*}{escapeinside=||}
|\checkmark| Project name: … <your-project-name>
|\checkmark| Add TypeScript? … No / Yes
|\checkmark| Add JSX Support? … No / Yes
|\checkmark| Add Vue Router for Single Page Application development? … No / Yes
|\checkmark| Add Pinia for state management? … No / Yes
|\checkmark| Add Vitest for Unit testing? … No / Yes
|\checkmark| Add an End-to-End Testing Solution? … No / Cypress / Playwright
|\checkmark| Add ESLint for code quality? … No / Yes
|\checkmark| Add Prettier for code formatting? … No / Yes

Scaffolding project in ./<your-project-name>...
Done.
\end{codeConsole*}
\switchcolumn
\begin{codeConsole}

\end{codeConsole}    
\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn

\switchcolumn[0]*%%%%%%%

\switchcolumn


\switchcolumn[0]*%%%%%%%

\switchcolumn


\end{paracol}
