\setcounter{section}{4}
\setcounter{subsection}{16}
\setcounter{subsubsection}{0}

\subsection{Capture Mode\\捕获模式}\label{subsec:capture}
\begin{docTcbKey}{capture}{=\meta{mode}}{no default, initially |minipage|}
The capture \meta{mode} defines how the box content is processed.

捕获模式\meta{mode}定义了如何处理盒子内容。

Feasible values for \meta{mode} are:

\meta{mode} 的可选值是：
\begin{itemize}
\item\docValue{minipage}:\\
  This is the default \meta{mode} for \refEnvLe{tcolorbox}.
  The content may have an upper and a lower part. 
  Optionally, the box
  can be \refKeyLe{/tcb/breakable}. The box content is put into a
  minipage or into something similar to a minipage.

这是 \refEnvLe{tcolorbox} 的默认 \meta{mode} 。%
内容可能有一个 |upper|和一个 |lower| 部分。%
可选地，盒子可以是 \refKeyLe{/tcb/breakable} 可分的。
盒子内容被放入一个 |minipage| 或类似于 |minipage| 的东西。
\item\docValue{hbox}:\\
  This is the default \meta{mode} for \refComLe{tcbox}. The content cannot have
  a lower part and cannot be broken. The colored box is sized according
  to the dimensions of the content.
  A shortcut to set this mode is \refKeyLe{/tcb/hbox}.

这是 \refComLe{tcbox} 的默认 \meta{mode} 。%
内容将没有lower部分，也不可分。%
盒子的大小根据内容的尺寸而定。%
设置此模式的快捷方式是 \refKeyLe{/tcb/hbox}.
\item\docValue{fitbox}:%
 (needs the \mylib{fitting} library)\\

 (需要启用 \mylib{fitting} 库)\\
 
 This is the default \meta{mode} for \refComLe{tcboxfit}. The content cannot have
  a lower part and cannot be broken.
  The content is sized according to the dimensions of the colored box.
  A shortcut to set this mode is \refKeyLe{/tcb/fit}.

这是 \refComLe{tcboxfit} 的默认 \meta{mode}。 %
盒子内没有lower部分，也不可分。
盒子的大小根据内容的尺寸而定。%
设置此模式的快捷方式是 \refKeyLe{/tcb/fit}.
\end{itemize}

\begin{exdispExample}{capture}
\tcbset{colframe=blue!75!black,colback=white}

\begin{tcolorbox}[capture=minipage]
|capture=minipage|\\
这是 \refEnvLe{tcolorbox} 的默认 \meta{mode} 。%
内容可能有一个 |upper|和一个|lower|部分。%
\tcblower
可选地，盒子可以是 \refKeyLe{/tcb/breakable} 可分的。
盒子内容被放入一个 |minipage| 或类似于 |minipage| 的东西。
\end{tcolorbox}

\begin{tcolorbox}[capture=hbox]
|capture=hbox|\\
内容将没有lower部分，也不可分。%
% \tcblower 使用会报错
盒子的大小根据内容的尺寸而定。而定而定而定而定而定%
\end{tcolorbox}

\begin{tcolorbox}[capture=fitbox,height=9mm]% needs the `fitting' library
|capture=fitbox|\\
内容将没有lower部分，也不可分。若忆阵梁架营买起玻匀器沿坦辫狐影葱锤湾鸣腾磁烂挺居介吩付条醒踩除笛博示戒没庙璃榴虎白椅益桃城季缠亩爷你员宫艇婆拨标塑浊考虏听枯驼谈呢浪迟屿骂慧郊室柏酬饰谱蝇渐锈辨秋胃嘱籍肆乙音本光鹅宣静惨刃前毁颜花竭若忆阵梁架营买起玻匀器沿坦辫狐影葱锤湾鸣腾磁烂挺居介吩付条醒踩除笛博示戒没庙璃榴虎白椅益桃城季缠亩爷你员宫艇婆拨标塑浊考虏听枯驼谈呢浪迟屿骂慧郊室柏酬饰谱蝇渐锈辨秋胃嘱籍肆乙音本光鹅宣静惨刃前毁颜花竭
%\footnote{译注，看这效果，是内容适应指定的高度等}%
\end{tcolorbox}
\end{exdispExample}
\end{docTcbKey}




\begin{docTcbKey}{hbox}{}{style, no default}
  % Shortcut for |capture=hbox|.
|capture=hbox| 的快捷方式。
\begin{exdispExample}{hbox}
\tcbset{colframe=blue!75!black,colback=white}

\begin{tcolorbox}[hbox]
This is a tcolorbox.
\end{tcolorbox}
\end{exdispExample}
\end{docTcbKey}


\begin{docTcbKey}{minipage}{}{style, no default}
  Shortcut for |capture=minipage|.

  |capture=minipage| 的快捷方式。
\end{docTcbKey}




% \clearpage
% Text Characteristics
% ① (trait) (of person) 特征 tèzhēng ; (of place, work) 特性 tèxìng
% ▸ a family characteristic
% 家族特征
% ② Mathematics [对数的] 首数 shǒushù
% 典型的 diǎnxíng de ‹feature›; 独特的 dútè de ‹behaviour, appearance, quality›