\begin{docTcbKey}{reset}{}{no value, initially set}
Sets (nearly) all |tcolorbox| settings (including loaded libraries) back to their default values
\emph{plus} any settings given by \refCom{tcbsetforeverylayer}.
\refKey{/tcb/savedelimiter}, \refKey{/tcb/capture}, and
\refKey{/tcb/shield externalize} keep their values.
Also, all raster values (see \Vref{sec:raster}) are not resetted.

设置(几乎)所有|tcolorbox|设置(包括已加载的库)回到它们的默认值，\emph{加上} 由\refCom{tcbsetforeverylayer}给出的任何设置.%
\refKey{/tcb/savedelimiter}, \refKey{/tcb/capture}, 和 \refKey{/tcb/shield externalize} 保持他们的值不变。%
此外，所有raster值(见\Vref{sec:raster})都不会重置。

This option is useful for boxes in boxes where the inner box should not inherit
the settings of the outer box.
Note that for boxes inside boxes the |reset| is done automatically, if the
standard settings of the package are used (v2.40 and above), see
Section \ref{subsec:everybox} from page \pageref{subsec:everybox}.

此项在嵌套的盒子中使用，可以重置从外部盒子继承过来的设置。%
注意，如果使用包的标准设置(v2.40及以上)，嵌套的内部盒子， |reset|会自动完成, 见\pageref{subsec:everybox}页的\ref{subsec:everybox}小节。
%See \refCom{tcbhighmath} for an example.
\end{docTcbKey}




\begin{docTcbKey}{code}{=\meta{code}}{no default, initially unset}
The given \meta{code} is executed immediately. This option is useful
to place some arbitrary code into an option list.

给定的\meta{code}立即执行。这个选项很有用，可以将一些任意代码放入选项列表中。
\begin{exdispExample}{code}
\tcbset{colback=red!5!white,colframe=red!75!black,
code={Useless at this spot but functional.},
fonttitle=\bfseries}

\begin{tcolorbox}[code={\newcommand{\mycommand}{\textit{working}}},
title=My \mycommand\ title]
This is a \textbf{tcolorbox}.
\end{tcolorbox}
\end{exdispExample}
\end{docTcbKey}



% \clearpage
\begin{docTcbKey}[][doc new=2016-10-21]{void}{}{no value, initially unset}
Annihilates the current |tcolorbox| as far as possible.
Basically, this comments out the whole |tcolorbox| by using a key.
If the option list of the current |tcolorbox| contains arbitrary code with global
impact (like counter settings), these actions are not undone automatically.
Nevertheless, the effects of \refKey{/tcb/phantom}, \refKey{/tcb/step},
\refKey{/tcb/new/auto counter}, etc., are removed by \refKey{/tcb/void}.

尽可能地摧毁当前的|tcolorbox|。基本上，通过使用关键字，将整个|tcolorbox|注释掉。如果当前|tcolorbox|的选项列表包含具有全局影响的任意代码（如计数器设置），则这些操作不会自动撤消。尽管如此，\refKey{/tcb/phantom}、\refKey{/tcb/step}、\refKey{/tcb/new/auto counter}等的效果将被\refKey{/tcb/void}移除。

%TODO 再翻译
% 尽可能消灭当前|tcolorbox|。%
% 基本上，就是一个设置，注释了整个|tcolorbox|盒子。%
% 如果当前|tcolorbox|的选项列表包含具有全局影响的任意代码(如计数器设置)，这些操作不会自动撤消。%
% 不过，\refKey{/tcb/phantom}, \refKey{/tcb/step},   \refKey{/tcb/new/auto counter}等的效果会被\refKey{/tcb/void}删除。

\begin{exdispExample}{void}
A%
\begin{tcolorbox}[
    title=This box is completely removed by the following key,
    void
]
This is a \textbf{tcolorbox}.
\end{tcolorbox}
B
\end{exdispExample}

\begin{marker}
This option key cannot be applied for every situation.
For example, if several box environments with the same environment name
are nested, for the outer environment \refKey{/tcb/void} cannot be used,
since the end of the inner environment will be misinterpreted as
end of the outer environment. Also, \refKey{/tcb/void} cannot be used
for environments wrapped with \refCom{tcolorboxenvironment}.

此选项键不能应用于每种情况。%
例如，如果嵌套了几个具有相同环境名称的盒子环境，外部环境不能使用\refKey{/tcb/void}。%
因为内部环境的结束会被误认为外部环境的终结。%
同样，\refKey{/tcb/void}不能用于由\refCom{tcolorboxenvironment}包装的环境。
\end{marker}
\end{docTcbKey}



% nirvana | BrE nɪəˈvɑːnə, AmE nərˈvɑnə,nɪrˈvɑnə |
% noun
% ① uncountable Religion 涅槃 nièpán
% ② countable (idyllic place) 极乐世界 jílè shìjiè ; (state) 无忧无虑的境界 wú yōu wú lǜ de jìngjiè

\begin{docTcbKey}[][doc new=2019-03-01]{nirvana}{}{no value, initially unset}
The contents of the current |tcolorbox| are processed including counter
settings, but the box is just not drawn.
Therefore, \refKey{/tcb/nirvana} is less radical than \refKey{/tcb/void}
and several box environments can be nested without problems.

当前|tcolorbox|的内容被处理，包括计数器设置，只有盒子没有绘制。%
因此， \refKey{/tcb/nirvana} 没有 \refKey{/tcb/void} 那么彻底，%
而且应用在嵌套的多个盒子环境上，不出问题。
\begin{exdispExample}{nirvana}
A%
\begin{tcolorbox}[
    title=This box is completely removed by the following key,
    nirvana
]
This is a \textbf{tcolorbox}.
\begin{tcolorbox}
Nested Box
\end{tcolorbox}
\end{tcolorbox}%
B
\end{exdispExample}
\end{docTcbKey}