\begin{docCommand}{tcbsetforeverylayer}{\marg{options}}
% \begin{stripedbox}
Sets options for every following \refEnvLe{tcolorbox} inside the current \TeX\ group.
In contrast to \refComLe{tcbset}, this does also
apply to nested boxes, see \Vref{subsec:everybox}.
Technically, the \meta{options} are appended to the default values for every
tcolorbox which are applied by \refKeyLe{/tcb/reset}.

% \tcblower
% 为当前\TeX\ 分组中的后续 \refEnvLe{tcolorbox} 设置选项。
% 与 tcbset 相比，这也适用于嵌套框，请参见 \Vref{subsec:everybox}.
% 从技术上讲,  \meta{options} 将附加到 \refKeyLe{/tcb/reset} 设置的 tcolorbox 的默认值。\par

在当前的\TeX\ 组中为每个后续的\refEnvLe{tcolorbox} 设置选项。与\refComLe{tcbset} 不同，它也适用于嵌套的盒子，请参阅 \Vref{subsec:everybox}。从技术上讲，\meta{options}将附加到每个通过 \refKeyLe{/tcb/reset} 应用的 tcolorbox 的默认值之后。%\parpar

\begin{引述之言}{virhuiai}
|\tcbsetforeverylayer|%
设置的选项，不受 |reset| 的影响。
\end{引述之言}

You should not use this macro, if you are not completely sure that you
want to have the \meta{options} also for boxes in boxes (in boxes in boxes \ldots).

% 如果您不完全确定也要为tcolorbox中的tcolorbox（的tcolorbox中\ldots）使用\meta{options}，则不应使用此宏。

如果您不确定是否希望在嵌套的盒子中（盒子中的盒子中的盒子\ldots）也使用\meta{options}，请不要使用此宏。
\begin{dispExample*}{sbs}
\begin{tcolorbox}[title=virhuiai家的盒子]
默认的盒子的内容
\end{tcolorbox}

\tcbset{colback=green!10!white}
\tcbsetforeverylayer{%
colframe=red!75!black}

\begin{tcolorbox}%
[title=All options for this box]
绿色的背景色\par\medskip
\begin{tcolorbox}[title=嵌套的盒子]
红色的边框，但没有绿色的背景色。
\end{tcolorbox}
\end{tcolorbox}
\bigskip

\begin{tcolorbox}[reset,%
title={reset的盒子}]
|\tcbsetforeverylayer|%
设置的选项，不受 |reset| 的影响。
\end{tcolorbox}

\begin{tcolorbox}[title=默认的盒子]
绿色的背景色
\end{tcolorbox}
\end{dispExample*}
\end{docCommand}
% Options given with |\tcbsetforeverylayer| survive a |reset|.