\newpage \suppressfloats
\nobackgroundcolor{t}
\nobackgroundcolor{b}
\nobackgroundcolor{l}
\nobackgroundcolor{r}
\nobackgroundcolor{g}
\backgroundcolor{c[0](4pt,4pt)(0.5\columnsep,4pt)}[rgb]{1,0.8,1}
\backgroundcolor{c[1](0.5\columnsep,4pt)(4pt,4pt)}[rgb]{1,1,0.8}
\backgroundcolor{C[0](10000pt,10000pt)(0.5\columnsep,10000pt)}[rgb]{1,0.8,1}
\backgroundcolor{C[1](0.5\columnsep,10000pt)(10000pt,10000pt)}[rgb]{1,1,0.8}

\subsection{Regions with Infinite Extensions\hfill 具有无限扩展的区域}
\label{sec:bgpaint-inf}

You are now seeing another \bgpaint{} much different from previous two
examples.  That is, after disabling painting of |t|, |b|, |l|, |r| and |g|
regions by \Uidx{\!\nobackgroundcolor!}, the author gave the followings
for painting this and the next pages.

现在你看到了另一个与前两个示例非常不同的\bgpaint{}。也就是说，在通过 \Uidx{\!\nobackgroundcolor!} 禁用|t|、|b|、|l|、|r|和|g|区域的绘制之后，作者为绘制本页和下一页给出了以下设置。

\begin{itemize}\item[]
|\backgroundcolor|
    |{c[0](4pt,4pt)(0.5\columnsep,4pt)}[rgb]{1,0.8,1}|\\
|\backgroundcolor|
    |{c[1](0.5\columnsep,4pt)(4pt,4pt)}[rgb]{1,1,0.8}|\\
|\backgroundcolor|
    |{C[0](10000pt,10000pt)(0.5\columnsep,10000pt)}[rgb]{1,0.8,1}|\\
|\backgroundcolor|
    |{C[1](0.5\columnsep,10000pt)(10000pt,10000pt)}[rgb]{1,1,0.8}|
\end{itemize}

\SpecialUsageIndex{\backgroundcolor}

The first two lines above is different from the previous declaration
because inside edges of |c[0]| and |c[1]| regions are shifted toward
outside of them and thus inside of unpainted |g| region so that the edges
are contacted.  On the other hand, the last two lines are for
\emph{under-painting} of columns and has \emph{\bginfext} to make top,
bottom and outside edges of |C| regions reaching to the corresponding
paper edges.  Since this under-painting is done with colors same as those
of over-painting of |c| regions, you will have an impression that the
paper is two-toned and \pwstuff{} are pasted on the paper\footnote{%
This footnote is given outside \env{paracol} environment but its
\bground{} is painted by light purple because it is merged with the
footnote \ref{fn:bgpaint-inf2}.\label{fn:bgpaint-inf1}}.

上面的前两行与之前的声明不同，因为|c[0]|和|c[1]|区域的内侧边缘向外移动，进入未绘制的|g|区域，使边缘相接触。另一方面，最后两行是用于对列进行\emph{下层绘制}，并且具有\emph{\bginfext}，使|C|区域的顶部、底部和外部边缘达到相应的纸张边缘。由于此下层绘制使用的颜色与|c|区域的上层绘制相同，所以你会有一种纸张是双色的，并且\pwstuff{}被粘贴在纸张上的印象\footnote{%
这个脚注是在\env{paracol}环境之外给出的，但是它的\bground{}被浅紫色绘制，因为它与脚注\ref{fn:bgpaint-inf2}合并了。\label{fn:bgpaint-inf1}}。
\par\bigskip

\begin{figure}\nosv
\def\arraystretch{0.8}
\centerline{\begin{tabular}[b]{|c|}\hline
    \hbox to.9\textwidth{}\\
    \parbox{.8\textwidth}{
This \texttt{f}(loat) region could be extended to both side edges
and the top edge of the paper if its extension were
\texttt{(10000pt,10000pt)(10000pt,-4pt)}.}\\
    \\\hline
    \end{tabular}}
\caption{A Page-Wise Figure \emph{Imported} from Pre-Environment}
\label{fig:bgpaint-inf}
\end{figure}

\begin{paracol}{2}
Though you cannot see, the right edge of this over-painted |c[0]| region
is shifted right by 4\,|pt| to hide the small patch at the right bottom
corner of the |p| region above by overlaying.

\switchcolumn
\begingroup\it
As explained in the right column, this {\rm|c[1]|} region also has an
invisible left edge shifted left by {\rm4\,|pt|}\footnote{

This (foot)|n|(ote) region could be extended to both side edges and the
bottom edge of the paper if its extension were
\texttt{(10000pt,-4pt)(10000pt,10000pt)}.\label{fn:bgpaint-inf2}}.
\endgroup

\switchcolumn*[\subsection*{This \texttt{s}(panning text) region could be
extended to both side edges of the paper if its extension were
\texttt{(10000pt,-4pt)}.}\par\medskip]

The author does not have much to say now for this column chunk.
\par\vfill

Still nothing to say particular to the page break we will have shortly.
\par\newpage

This paragraph is just for keeping the \env{paracol} environment alive in
this page.
\switchcolumn

\begingroup\it
Little to say as well.
\par\vfill

Nothing to say as well.
\par\newpage

This paragraph is not necessary for keeping alive the environment but is
given for consistent view.
\endgroup

\begin{figure*}\nosv
\def\arraystretch{0.8}
\centerline{\begin{tabular}[b]{|c|}\hline
    \hbox to.9\textwidth{}\\
    \parbox{.8\textwidth}{
This figure is given in the \env{paracol} environment closed in the
previous page but its background is not painted.}\\
    \\\hline
    \end{tabular}}
\caption{A Page-Wise Figure \emph{Exported} to Post-Environment}
\label{fig:bgpaint-inf2}
\end{figure*}
\end{paracol}
\bigskip

Note that overlay painting is inevitable for two-toned page painting, as
far as you want to paint \bground{} of \pwstuff.

请注意，如果您希望绘制\pwstuff{}的\bground{}，那么对于双色页面绘制，覆盖绘制是不可避免的。

The last issue of \bgpaint{} is about painting materials given outside
\env{paracol}.  As you have seen, \Preenv{} and \postenv{} are painted but
it is done only when they reside in a page having a portion of a
\env{paracol} environment (maybe) of course.  Therefore, the next page is
\emph{not} painted because the page does not have any parallel-columned
stuff.  Therefore, even if you wish to paint the whole of your document
including pages without \env{paracol} stuff, you cannot do it just with
\Paracol{} package, at least so far.

\bgpaint{}的最后一个问题是关于在\env{paracol}之外给出的材料的绘制。正如您所见，\Preenv{}和\postenv{}是被绘制的，但只有当它们位于具有\env{paracol}环境（可能）的页面中时才进行绘制。因此，下一页\emph{不会}被绘制，因为该页没有任何平行列的内容。因此，即使您希望绘制整个文档，包括没有\env{paracol}内容的页面，至少目前您无法仅使用\Paracol{}宏包来实现。

On the other hand, some materials given outside \env{paracol} environments
are painted as if they are given in the environment when they are
\emph{imported} into the environment.  One category has footnotes given in
\preenv{} when \!\footnotelayout!|{m}| is specified for merging, as
exemplified by the footnote \ref{fn:bgpaint-inf1} in the previous page.
Note that such a footnote is painted by the color for |n| region rather
than |p| region even when there are no footnotes in the \env{paracol}
environment.  The other category has ordinary floats given by \env{figure}
and/or \env{table}
(i.e., neither \env{figure*} nor \env{table*}) environments outside
\env{paracol} and then \emph{deferred} to a page having (a portion of)
stuff produced by \env{paracol}.  Since such a float, e.g.,
Figure\Tie\ref{fig:bgpaint-inf} in this page, is considered as a page-wise
float given in the \env{paracol} environment in this section, its
background is painted by the color for the |f| region, rather than that
for the |p| region which would be used if the float were is placed in the
previous page.  Note that such a deferred float import could occur not
only from the page having \beginparacol{} but also from pages preceding
it.  For example, if you have three \env{figure} environments in a page
$p-1$ just preceding the page $p$ in which you start a \env{paracol}
environment, it could happen that first one is placed in $p-1$ without
painting, the second is placed in $p$ and painted by the color for |p|,
and the third is placed in $p+1$ and painted by the color for |f|.

另一方面，一些在\env{paracol}环境之外给出的材料在被\emph{导入}到环境中时会被绘制，就好像它们是在环境中给出的一样。一个类别是在\preenv{}中给出的，在指定 \!\footnotelayout!|{m}|进行合并时的脚注，例如前一页的脚注\ref{fn:bgpaint-inf1}。请注意，即使在\env{paracol}环境中没有脚注，这样的脚注也会使用|n|区域的颜色而不是|p|区域的颜色进行绘制。另一类是由\env{figure}和/或\env{table}（即既不是\env{figure*}也不是\env{table*}）环境给出的普通浮动体，然后被\emph{延迟}到由\env{paracol}产生的（部分）内容的页面。因为这样的浮动体，例如本页的Figure\Tie\ref{fig:bgpaint-inf}，被认为是在本节的\env{paracol}环境中给出的整页浮动体，所以它的背景会使用|f|区域的颜色进行绘制，而不是如果该浮动体放在前一页上时将使用|p|区域的颜色。请注意，这样的延迟浮动体导入不仅可能来自具有\beginparacol{}的页面，也可能来自之前的页面。例如，如果在您开始一个\env{paracol}环境的页面$p$的前一页$p-1$中有三个\env{figure}环境，可能发生以下情况：第一个放置在$p-1$中而没有绘制，第二个放置在$p$中并使用|p|的颜色进行绘制，第三个放置在$p+1$中并使用|f|的颜色进行绘制。


Finally some materials \emph{exported} from a \env{paracol} environment
are painted as if they are in \postenv.  In previous two subsections, we
saw \Mgfnote{}s (e.g., \ref{fn:bgpaint1} in p.\Tie\pageref{fn:bgpaint1}
and \ref{fn:bgpaint-me1} in p.\Tie\pageref{fn:bgpaint-me1}) are painted by
the color of |p| rather than |n|.  The other kind of exportation is of
page-wise floats given in a \env{paracol} environment but deferred to the
page next to the page having \Endparacol, or further.  For example,
Figure~\ref{fig:bgpaint-inf2} is given in the \env{paracol} environment
above in this page, but its \bground{} is not painted because the next page
in which the figure is placed does not have any parallel-columned
stuff\footnote{%
If it has, the background is painted by the color for |p|.}.

最后，一些从\env{paracol}环境中\emph{导出}的材料被绘制，就好像它们在\postenv{}中一样。在前两个小节中，我们看到\Mgfnote{}（例如，\pageref{fn:bgpaint1}页上的\ref{fn:bgpaint1}和\pageref{fn:bgpaint-me1}页上的\ref{fn:bgpaint-me1}）被绘制为|p|区域的颜色，而不是|n|。另一种导出的类型是在\env{paracol}环境中给出的整页浮动体，但是延迟到\Endparacol{}所在页面的下一页或更后面的页面。例如，本页上方的\env{paracol}环境中给出了Figure~\ref{fig:bgpaint-inf2}，但是它的\bground{}没有被绘制，因为放置该图的下一页没有任何平行列的内容\footnote{如果有，背景将使用|p|区域的颜色进行绘制。}。

\newpage\vspace*{\fill}
\centerline{(intentionally blanked page to show this page is \emph{not}
painted)}
\vfill
\advance\skip\footins-4pt\relax