\section{Column Synchronization\\栏同步}\label{sec:sync}

\columnratio{0.3,0.42,0.28}
\begin{paracol}{3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{VerbatimII}
\columnratio{0.3,0.42,0.28}
\begin{paracol}{3}
第1栏
\switchcolumn
第2栏
\switchcolumn
第3栏

\switchcolumn[0]*
同步 ...
\switchcolumn
...
\end{paracol}  
\end{VerbatimII}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\switchcolumn
The \!\switchcolumn! command may also be followed by a `|*|' to
{\em\Uidx\sync{}e} columns.  After you switch from a column to another by
\!\switchcolumn!|*| (or \!\switchcolumn!|[|$i$|]*|), all the columns are
vertically aligned at the bottom of the {\em deepest} one preceding the
command.  For example, the previous section has three \!\switchcolumn!|*|
commands at which left and right columns are vertically aligned.
\switchcolumn
\!\switchcolumn! 命令后面可以加上 `|*|'，用来{\em 同步}栏。当你使用 \!\switchcolumn!|*|（或 \!\switchcolumn!|[|$i$|]*|）从一栏切换到另一栏时，所有栏都会垂直对齐在该命令之前最{\em 深}的栏的底部。例如，前一节使用了三个 \!\switchcolumn!|*| 命令，使左右两栏垂直对齐。

\switchcolumn[1]
The {\em starred} version of \!\switchcolumn! may have an optional
argument to specify a single-column {\em\Uidx\mctext} whose bottom is the
vertical alignment point of columns.  For example, \!\section!
commands in this manual are given as optional arguments
of \!\switchcolumn!|*| like;
\switchcolumn
{\em 带星号}版本的 \!\switchcolumn! 命令可以带有可选参数，用来指定一个单栏的{\em 同步文本}，其底部作为栏的垂直对齐点。例如，本手册中的 \!\section! 命令作为 \!\switchcolumn!|*| 的可选参数给出，如下所示：

\switchcolumn[1]
\begin{Verbatim}
\switchcolumn*[\section{Basic Usage}]
\end{Verbatim}
\switchcolumn
\begin{Verbatim}
\switchcolumn*[\section{基础用法}]
\end{Verbatim}
\switchcolumn[1]
The \env{paracol} environment may also start with a \mctext{} by
specifying it as the optional argument of \!\begin!|{|\env{paracol}|}|.
For example, at the beginning of this document, the author put;
\switchcolumn
\env{paracol} 环境也可以以一个 \mctext{} 开始，将其指定为 \!\begin!|{|\env{paracol}|}| 的可选参数。例如，在本文档的开头，作者使用了以下代码：

\switchcolumn[1]*
\begin{Verbatim}
\begin{paracol}{2}[\section{Introduction}]
\end{Verbatim}

\switchcolumn
\begin{Verbatim}
\begin{paracol}{2}[\section{介绍}]
\end{Verbatim}

\end{paracol}    
\end{document}%%%%%%