\section{Two-Sided Typesetting and Parallel-Paging\hfill 双面排版和并列分页}
\label{sec:ppts}

This and the next section are typeset with \Uidx{\!\twosided!} enabling
features |p|, |c| and |m| and also |b| for a part of the next section.
The effect of |p| feature can be seen by the \oddeven{left}{right}, or in
other word inside, margin of this \oddeven{odd}{even}-numbered page is
narrower than that of the previous pages because the author reduced the
effective \oddeven{left}{right} side margin being calculated from
\oddeven{\cs{oddsidemargin}}{\cs{evesidemargin}}

这一节和下一节使用 \Uidx{\!\twosided!} 启用特性|p|、|c|和|m|，以及部分下一节的特性|b|进行排版。通过查看此\oddeven{奇数}{偶数}页的内边距，可以看到|p|特性的效果，即比前面的页面的内边距更窄，因为作者减小了从 \oddeven{\cs{oddsidemargin}}{\cs{evesidemargin}} 计算出的有效 \oddeven{left}{right} 边距。


\SpecialIndex{\oddsidemargin}
\SpecialIndex{\evensidemargin} 

by 75\,\%\footnote{ 
This document itself does not have |twoside| option in its
\!\documentclass! but the inconsistency between the option and
\!\twosided! is not visible because \!\pagestyle! is |plain|.}.
This setting makes the \oddeven{right}{left} side or outside margin of
this page enlarged by 125\,\%, as well as the \oddeven{left}{right} side
and outside margin of the next \oddeven{even}{odd}-numbered page specified
by \oddeven{\cs{evensidemargin}}{\cs{oddsidemargin}}.

由于75\,\%的设置\footnote{%
此文档本身在其 \!\documentclass! 中没有 |twoside| 选项，但是选项与 \!\twosided! 之间的不一致之处并不可见，因为 \!\pagestyle! 是 |plain|。}。
这个设置使得本页的\oddeven{右}{左}边缘或外侧边缘增大了125,%，以及下一页的\oddeven{左}{右}边缘和外侧边缘，由 \oddeven{\cs{evensidemargin}}{\cs{oddsidemargin}} 指定的\oddeven{偶数}{奇数}页。

Next, we see the effects of |c| and |m| features by the \env{paracol}
environment below for which \Uidx{\!\columnratio!}|{0.6}| and
\Uidx{\!\marginparthreshold!}|{0}| are declared to make the \emph{inside}
columns (\oddeven{left}{right} ones in \oddeven{odd}{even}-numbered pages)
are wider than the \emph{outside} ones and all marginal notes go to
outside (\oddeven{right}{left} in \oddeven{odd}{even}-numbered pages)
margins.

接下来，我们看到以下 \env{paracol} 环境通过 \Uidx{\!\columnratio!}|{0.6}| 和  \Uidx{\!\marginparthreshold!}|{0}| 来实现 |c| 和 |m| 特性的效果，使得\emph{内部}列（在\oddeven{奇数}{偶数}页中的\oddeven{左}{右}列）比\emph{外部}列更宽，并且所有的边注都放在外侧边缘（在\oddeven{奇数}{偶数}页中的\oddeven{右}{左}边缘）。

\columnratio{0.6}\marginparthreshold{0}

\par\Hrule
\begin{paracol}{2}
\switchcolumn
\footnotetext*{Since the author is temporarily disabling the warning from
marginal note placement mechanism of \LaTeX, pushing down the second
marginal note from column-1 is silently performed when you process this
document.}
\switchcolumn
This line\Marginpar{First marginal note from column-0.} of the first
paragraph of the inside column-0 has a marginal note.  Now the author puts
a few dummy lines to keep a space below the marginal note.\\
\Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\
\Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\par

This line\Marginpar{Second marginal note from column-0.} of the second
paragraph of the inside column-0 also has a marginal note.  Now the author
puts a few dummy lines again but this time to go down to the bottom of the
page.\\
\Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\
\Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\
\Dotfill\\ \Dotfill\par

This is the third paragraph of the inside column-0 having a page break in 
it.  Since shortly we will be in an \oddeven{even}{odd}-numbered page
\pageref{page:ppts2} (now), this wider column\Marginpar{Third marginal
note from column-0} is now \oddeven{right}{left} one keeping it
inside, while the marginal note given in the first line of this page goes
to \oddeven{left}{right} and outside.  Now we will have a \!\switchcolumn!
below this paragraph to go to the column-1 and back to the previous page
\pageref{sec:ppts}.\label{page:ppts2}
\switchcolumn
\it
This is the first paragraph in the narrower, italicized and outside
column-1.  In this paragraph, we shortly have a marginal note, italicized
too, which goes to the outside margin shared by all marginal notes from
both columns.\Marginpar{\it First marginal note from column-1.}  The
marginal note given here is placed its natural position and its first line
is aligned to the first line of the second sentence of this paragraph by
exploitation of the space between two marginal notes from the column-0,
though we already have had three notes from the column.

Now\Marginpar{\it Second marginal note from column-1.} the author puts
another marginal note whose first line would be aligned to that of this
paragraph, but it is pushed down below the second marginal note from the
column-0 because two notes conflict with each other over the
space\footnotemark*[+0].  Note that since the note from this column is given
\emph{after} that from the column-0 was given, the conflict is solved
pushing the note from this column down rather than that from the
column-0.  Now the author puts a few dummy lines to go to the second last
line of this page.\\
\Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\ \Dotfill\\
\Dotfill\par

This is the third paragraph of the outside column-1, which becomes
\oddeven{left}{right} shortly by the page break.\Marginpar{\it Third
marginal note from column-1.}  The third marginal note is given in the
first line of this page, but it is pushed down again due to the conflict
with the note from the column-0.
\end{paracol}
\Hrule

Note that the position of the last marginal note in the \env{paracol}
\Marginpar{Marginal note given after \env{paracol} environment is closed.}
environment which we just have closed affects the marginal note placement
in \postenv.  For example, the marginal note given in the first line of
this paragraph is pushed down.

请注意，在我们刚刚关闭的\env{paracol}环境中，最后一个边注的位置会影响\postenv 中的边注位置。例如，给出在本段落第一行的边注会被推下去。


\ifodd\value{page}
We will see a few examples of \parapag{}ing shortly, but before that we
will have an intentional black page to make the first page of the example
odd-numbered to avoid you have an impression that its layout is
incorrect\footnote{At least the author himself had such impression without the blank page.}
because if it were in an even page you would see the {\em outside\/} third
and fourth supplementary {\em columns\/} at first.

不久我们将看到一些\parapag{}的例子，但在此之前，我们将有一个有意留白的页面，使示例的第一页成为奇数页，以避免给您一种布局错误的印象\footnote{至少在没有空白页面的情况下，作者本人也有这样的印象。}，因为如果它在偶数页，您将首先看到第三和第四个辅助{\em 列}的{\em 外侧}。
\newpage\vspace*{\fill}\centerline{(intentionally blanked page)}\vfill

\else
From the next page, we will see a few examples of \parapag{}ing.

从下一页开始，我们将看到一些\parapag{}的例子。
\fi
