\section{Numbering and Placement of Page-Wise Footnotes\hfill 页注的编号和位置}
\label{sec:fnnp}
\columnratio{0.55}
\begin{paracol}{2}
Here we have a simple example of \scfnote{} but not-merged
footnotes\footnote{
Because of the non-merged typesetting, this footnote is put above the
example.\par\Hrule\label{fn:preenv}}.
\switchcolumn
这里有一个简单的示例，展示了非合并的\scfnote{}脚注\footnote{因为不是合并的排版方式，所以这个脚注放在了示例之上。\par\Hrule\label{fn:preenv}}。
\end{paracol}

\begin{Verbatim}
\footnotelayout{p}
\end{Verbatim}
\footnotelayout{p}
\begin{paracol}{2}
\fnpar{First left-column 左列第一}{\footnote{First left-column footnote. 左列第一脚注。}}
\fnpar{Second left-column 左列第2}{\footnote{Second left-column footnote. 左列第2脚注。}}
\switchcolumn
\fnpar{First right-column}{\footnote{First right-column footnote.}}
\fnpar{Second right-column}{\footnote{Second right-column footnote.
This and all other footnotes above are \scfnote{} and, since footnote
typesetting is non-merged, they are put above the \postenv.右列第二脚注。这个脚注和上面的所有脚注都是\scfnote{}，由于脚注排版是非合并的，它们放在了\postenv{}之上。 }}
\end{paracol}
\Hrule

\columnratio{0.55}
\begin{paracol}{2}
As shown above, it is easy to have a reasonable result of footnote
numbering and placement as far as your \env{paracol} environment is
completely included in a page and you accept the numbering in
left-column-first manner constructing the environment as follows
exploiting the fact \counter{footnote} is made global, where $b$ is the
value of \counter{footnote} counter at \beginparacol, i.e., the number
given to the footnote just preceding the environment, and thus
$b=\ref{fn:preenv}$ in the example above.
\begin{quote}\vskip-1pt
|\begin{paracol}{2}|\\
\textit{left-column stuff having $n$ footnotes numbered $b+1$, $b+2$,
\ldots, $b+n$}\\
|\switchcolumn|\\
\textit{right-column stuff having $m$ footnotes numbered $b+n+1$, $b+n+2$,
\ldots, $b+n+m$}\\
|\end{paracol}|
\end{quote}\vskip-1pt
\switchcolumn
如上所示，只要您的 \env{paracol} 环境完全包含在一页中，并且您接受按左列优先的方式编号和放置脚注，那么脚注编号和放置的结果就会比较合理。可以通过以下方式构建环境，利用 \counter{footnote} 是全局的这一事实，其中 $b$ 是在 \beginparacol 处的 \counter{footnote} 计数器的值，即在环境之前的脚注的编号，因此在上面的示例中 $b=\ref{fn:preenv}$。
\begin{quote}\vskip-1pt
|\begin{paracol}{2}|\\
\textit{left-column stuff having $n$ footnotes numbered $b+1$, $b+2$,
\ldots, $b+n$}\\
|\switchcolumn|\\
\textit{right-column stuff having $m$ footnotes numbered $b+n+1$, $b+n+2$,
\ldots, $b+n+m$}\\
|\end{paracol}|
\end{quote}\vskip-1pt
\switchcolumn[0]*
The real life is, however, tougher than that, because the assumptions above
are too optimistic as described in the following subsections.
\switchcolumn
然而，现实生活比上面的假设更加艰难，因为如下小节所描述的那样，这些假设过于乐观。
\end{paracol}
\vskip-3pt\vskip0pt