

\subsection{Page-Wise Footnotes}
\label{sec:ref-scfnote}

\begin{description}
\item[\Midx{\!\footnotelayout!}\marg{layout}]\mbox{}\par
\columnratio{0.55}
\begin{paracol}{2}
The command specifies the \meta{layout}${}\in\{|c|,|p|,|m|\}$ of footnotes
in \env{paracol} environments as follows.
\switchcolumn
该命令指定了在\env{paracol}环境中脚注的 \meta{layout}${}\in\{|c|,|p|,|m|\}$，具体如下。
\end{paracol}

\begin{description}
\columnratio{0.55}
\begin{paracol}{2}
\item[|c|\rm(\textit{olumn})] makes footnotes {\em\Uidx\mcfnote} (aka
multi-columned) being default to place footnotes in each column at the
bottom of the column and separating them from \Preenv{} and \Postenv{}
footnotes.
\switchcolumn\item[|c|\rm(\textit{olumn})]
使脚注{\em\Uidx\mcfnote}（也称为多列脚注）默认在每列底部放置脚注，并将其与 \Preenv{} 和 \Postenv{} 的脚注分开。
\switchcolumn[0]*
\item[|p|\rm(\textit{age})] makes footnotes {\em\Uidx\scfnote} (aka
single-columned) so that footnotes in all columns are gathered, typeset
spanning all columns, and placed at the bottom of the page in which they
appear or at the end of the \env{paracol} environment they belong to, so
that they are separated from \Preenv{} and \Postenv{} footnotes.
\switchcolumn\item[|p|\rm(\textit{age})]
将脚注设置为{\em\Uidx\scfnote}（也称为单列脚注），以便将所有列中的脚注聚集在一起，跨越所有列进行排版，并放置在它们所在的页面底部，或者放置在它们所属的\env{paracol}环境的末尾，以便与\Preenv{}和\Postenv{}脚注分开。
\switchcolumn[0]*
\item[|m|\rm(\textit{erge})] makes \Scfnote{}s {\em\Uidx\mgfnote} with
footnotes in outside of the environment but in the same page, i.e., those
in \Preenv{} and \postenv.
\switchcolumn\item[|m|\rm(\textit{erge})]
在同一页的环境外但在相同页面中，即\Preenv{}和\postenv{}中，使用\Scfnote{}和{\em\Uidx\mgfnote}创建脚注。
\end{paracol}
\end{description}


\begin{itemize}
\columnratio{0.55}
\begin{paracol}{2}
\item
An example of \Mgfnote{} is found in p.~\pageref{sec:ref-paracol} while
you will see many of them in Section~\ref{sec:fnnp}\footnote{

The left-column footnote \ref{fn:flush} in p.~\pageref{fn:flush} looks like
a merged footnote because it is at the bottom of the page and the marked
text is above the single-column text.  However, it is an ordinary
\mcfnote{} one produced by a trick with \cs{footnotemark} and
\cs{footnotetext} in different \env{paracol} environments.}.
\switchcolumn\item
在第~\pageref{sec:ref-paracol} 页中可以找到 \Mgfnote{} 的一个示例，而在第~\ref{sec:fnnp} 节中则会看到许多这样的示例\footnote{在第~\pageref{fn:flush} 页的左列脚注 \ref{fn:flush} 看起来像是一个合并的脚注，因为它位于页面底部，而标记的文本位于单列文本之上。然而，它是由在不同的\env{paracol}环境中使用\cs{footnotemark}和\cs{footnotetext}技巧生成的普通\mcfnote{}脚注。}。
\switchcolumn[0]*
\item
In any layouts, a footnote cannot have page breaks in it, i.e., a footnote
is always put in a page as a whole.  This makes it impossible to have a
footnote taller than \!\textheight! and thus you will see a warning
message if you give a very long footnote which will be printed intruding
into the area for page footer (or out of the paper bound).
\switchcolumn\item
在任何布局中，脚注不会出现分页，即脚注总是作为一个整体放在一页中。这意味着脚注的高度不可能超过 \!\textheight!，因此如果您给出一个非常长的脚注，它将打印出超出页面页脚区域（或超出纸张边界）的警告消息。
\switchcolumn[0]*
\item
Choosing the layout |p|age-wise or |m|erged makes \counter{footnote}
counter global and \!\fncounteradjustment!  shown below performed inside
\!\footnotelayout!.  Choosing |c|olumn-wise let the command do the
operations oppositely, i.e., localizes \counter{footnote} and does
\!\nofncounteradjustment!.  Though these settings are usually appropriate
for each footnote layout but you can override them by explicitly using
commands like \!\localcounter!|{footnote}|.
\switchcolumn\item
选择布局为|p|age-wise或|m|erged会使\counter{footnote}计数器变为全局，并在 \!\footnotelayout! 内执行下面的 \!\fncounteradjustment! 操作。选择|c|olumn-wise会使命令执行相反的操作，即将\counter{footnote}局部化并执行 \!\nofncounteradjustment!。虽然这些设置通常适用于每个脚注布局，但您可以通过显式使用 \!\localcounter!|{footnote}| 等命令来覆盖它们。
\switchcolumn[0]*
\item
The command has to be outside of \env{paracol} environments to decide the
action in the environments following them.  If it appears in a
\env{paracol} environment, you will have a warning message saying it is
ignored.
\switchcolumn\item
该命令必须放在\env{paracol}环境之外，以决定其后的环境中的操作。如果它出现在\env{paracol}环境中，你将收到一个警告消息，表示该命令被忽略。
\switchcolumn[0]*
\item
\changes{v1.3-5}{2013/09/17}
{Remove description of \cs{multicolumnfootnotes},
\cs{singlecolumnfootnotes}, \cs{mergedfootnotes} but mention they
are still available.}

In old versions of \Paracol, namely 1.2 and its minor revisions 1.2x,
footnote layout was controlled by a set of lengthy commands
\Midx{\!\multicolumnfootnotes!} for |c|, \Midx{\!\singlecolumnfootnotes!}
for |p|, and \Midx{\!\mergedfootnotes!} for |m|.
Though they are still available and will be so forever for backward
compatibility, it is recommended to use \!\footnotelayout!\footnote{

Not only for type saving but also for being familiar with this command
which could have some advanced feature, for example to put gathered
footnotes into a specific column, someday.}.
\switchcolumn\item
在旧版本的 \Paracol 中（即 1.2 版本及其小修订版本 1.2x），脚注布局由一组冗长的命令控制：\Midx{\!\multicolumnfootnotes!} 用于 |c|，\Midx{\!\singlecolumnfootnotes!} 用于 |p|，\Midx{\!\mergedfootnotes!} 用于 |m|。虽然它们仍然可用，并且将永远保持向后兼容，但建议使用 \!\footnotelayout!\footnote{不仅为了节省输入，还为了熟悉这个命令，它可能具有一些高级功能，例如将收集的脚注放入特定的列中。}。
\switchcolumn[0]*
\item
It must be $\meta{layout}\in\{|c|,|p|,|m|\}$, or you will have an error
message of illegal layout specifier.
\switchcolumn\item
必须是 $\meta{layout}\in\{|c|,|p|,|m|\}$，否则您将收到非法布局说明符的错误消息。
\end{paracol}

\end{itemize}

\KeepSpace{5}
\item[\Midx{\!\footnote!}\texttt{*}\oarg{num}\marg{text}]\mbox{}
\Item[\Midx{\!\footnotemark!}\texttt{*}\oarg{num}]\mbox{}
\Item[\Midx{\!\footnotetext!}\texttt{*}\oarg{num}\marg{text}]\mbox{}\par
\columnratio{0.55}
\begin{paracol}{2}
The starred version of \!\footnote!, \!\footnotemark! and \!\footnotetext!
are for the adjustment of the footnote numbering, the order of footnote
marks in main texts, and the stacking order of footnotes at page
bottom.  Their usages with various examples are given in
Section~\ref{sec:fnnp}.
\switchcolumn
\!\footnote!、\!\footnotemark! 和 \!\footnotetext! 的星号版本用于调整脚注编号、主文本中脚注标记的顺序以及页面底部脚注的堆叠顺序。其各种示例的用法详见第~\ref{sec:fnnp}节。    
\end{paracol}


\KeepSpace{3}
\item[\Midx{\!\fncounteradjustment!}]\mbox{}
\Item[\Midx{\!\nofncounteradjustment!}]\mbox{}\par
\columnratio{0.55}
\begin{paracol}{2}
The maintenance of \counter{footnote} with the starred footnote commands
such as \!\footnote!|*| shown above causes out-of-order progress of the
counter to make it hard to have a consistent counter value at
\Endparacol.  The command \!\fncounteradjustment! is to let \Endparacol{}
adjust the value of the counter based on its value at
\beginparacol{} and the number of footnote commands in the environment.
The command \!\nofncounteradjustment! is to tell \Endparacol{} to do
nothing as in default.
\switchcolumn
使用上面展示的带星号的脚注命令（如 \!\footnote!|*| ）来维护\counter{footnote}会导致计数器的顺序进展混乱，使得很难在\Endparacol{}处获得一致的计数器值。命令 \!\fncounteradjustment! 用于让\Endparacol{}根据其在\beginparacol{}处的值和环境中脚注命令的数量来调整计数器的值。命令 \!\nofncounteradjustment! 用于告诉\Endparacol{}不做任何调整，这是默认情况下的行为。
\end{paracol}
\begin{itemize}
\columnratio{0.55}
\begin{paracol}{2}
\item
Though \!\footnotelayout! with |p|(age-wise) or |m|(erged) argument does
\!\fncounteradjustment! while that with |c|(olumn) does
\!\nofncounteradjustment! inside of it, you can override these settings by
explicitly putting a counter adjustment command after \!\footnotelayout!.
\switchcolumn\item
尽管使用|p|(age-wise)或|m|(erged)参数的 \!\footnotelayout! 会在其中执行 \!\fncounteradjustment!，而使用|c|(olumn)的 \!\footnotelayout! 会执行 \!\nofncounteradjustment!，但您可以通过在 \!\footnotelayout! 之后显式放置计数器调整命令来覆盖这些设置。
\switchcolumn[0]*
\item
The effect of \!\fncounteradjustment! is shown in Section~\ref{sec:fnnp}.
\switchcolumn\item
\!\fncounteradjustment! 的效果在第~\ref{sec:fnnp}~节中展示。
\end{paracol}
\end{itemize}


\item[\Midx{\!\belowfootnoteskip!}]\mbox{}\par
\columnratio{0.55}
\begin{paracol}{2}
The typesetting parameter specifies the amount of the space inserted below
footnotes of single-column \preenv{} if it does not have bottom floats.  The
default amount is 0\,pt, i.e., no space is added.
\switchcolumn
typesetting参数指定了在单列\preenv{}的脚注下方插入的空间量，如果它没有底部浮动对象。默认的量是0,pt，即不添加任何空间。
\end{paracol}
\end{description}
