\begin{parcolumns}[colwidths={1=\parcolumnsLeft}]{2}% 设置为两栏排版
\colchunk{在你的内心深处，你一直知道你注定要学习
Clojure。每次你举起键盘，对难以理解的类层次结构感到痛苦；每次你在夜晚醒着，因为一个由突变引发的
Heisenbug
而令你的亲人痛苦；每次一个竞态条件使你拔出更多的你已经越来越少的头发，你内心的某个秘密部分总是知道{\tt 肯定有更好的办法}。}
\colchunk{Deep in your \csh一音标{Innermost}{/ˈɪnərmoʊst/}%：最内部的
\ \csh一音标{being}{/ˈbiːɪŋ/ 存在}, you've always known you were \csh一音标{destined}{/ˈdɛstɪnd/ 注定的} to
learn Clojure. Every time you held your keyboard \csh一音标{aloft}{/əˈlɔːft/ 在空中，向上}, crying out in
\csh一音标{Anguish}{/ˈæŋɡwɪʃ/：痛苦} over an \csh一音标{Incomprehensible}{/ˌɪnkɑːmprɪˈhɛnsɪbəl/：难以理解的} class \csh一音标{Hierarchy}{/ˈhaɪəˌrɑːrki/：层次结构}; every time you lay
awake at night, \csh一音标{Disturbing}{/dɪˈstɜːrbɪŋ/：令人不安的} your loved ones with \csh一音标{Sobs}{/sɑːbz/：抽泣} over a
\csh一音标{Mutation}{/mjuːˈteɪʃən/：突变}-induced \csh一音标{heisenbug}{/ˈhaɪzənbʌɡ/ 海森堡虫\footnotemark[1]}; every time a \csh一音标{race condition}{/reɪs kənˈdɪʃən/ 竞态条件\footnotemark[2]} caused you to
pull out more of your \csh一音标{everdwindling}{/ˈɛvər dwɪndlɪŋ/ 不断减少的} hair, some secret part of you has
known that \emph{there has to be a better way}.
% Deep in your innermost being, you've always known you were destined to
% learn Clojure. Every time you held your keyboard aloft, crying out in
% anguish over an incomprehensible class hierarchy; every time you lay
% awake at night, disturbing your loved ones with sobs over a
% mutation-induced heisenbug; every time a race condition caused you to
% pull out more of your ever-dwindling hair, some secret part of you has
% known that \emph{there has to be a better way}.
}
\footnotetext[1]{一种在尝试调试时会改变行为的计算机bug}%todo 后面去那边文档添加
\footnotetext[2]{计算机科学中关于资源争夺的问题}
\end{parcolumns}


\begin{parcolumns}[colwidths={1=\parcolumnsLeft}]{2}% 设置为两栏排版
\colchunk{现在，终于，你面前的这个教材将会将你与你一直渴望的编程语言结合在一起。}
\colchunk{Now, at long last, the \csh一音标{Instructional}{/ɪnˈstrʌkʃənəl/}%：教学的
\ \csh一音标{Material}{/məˈtɪriəl/} %：材料，资料
you have in front of your
face will \csh一音标{Unite}{/juːˈnaɪt/：联合，结合} you with the programming language you've been \csh一音标{Longing}{/ˈlɔːŋɪŋ/：渴望}
for.}
\end{parcolumns}


\section[学习新的编程语言：穿越四个迷宫的旅程]{学习新的编程语言：穿越四个迷宫的旅程\\Learning a New Programming Language: A Journey Through the Four Labyrinths}

\begin{parcolumns}[colwidths={1=\parcolumnsLeft}]{2}% 设置为两栏排版
\colchunk{为了最大限度地掌握 Clojure，你必须克服学习新语言所面临的四个挑战：}
\colchunk{To \csh一音标{Wield}{/wiːld/：掌握，使用} Clojure to its fullest, you'll need to find your way through
the four \csh一音标{Labyrinths}{/ˈlæbərɪnθs/：迷宫} that face every programmer learning a new language:}
\end{parcolumns}

\begin{parcolumns}[colwidths={1=\parcolumnsLeft}]{2}% 设置为两栏排版
\colchunk{
\begin{description}
    \item [工具森林] 一个友好且高效的编程环境使得尝试你的想法变得简单。你将会学习如何设置你的环境。
    \item[语言之山] 当你攀登这座山时，你会学会 Clojure
的语法、语义和数据结构的知识。你将会学习如何使用最强大的编程工具之一，宏，以及如何使用
Clojure 的并发构造来简化你的生活。
\item[人工制品之洞]
在其深处，你将学习构建、运行和分发你自己的程序，以及如何使用代码库。你还将了解
Clojure 与 Java 虚拟机（JVM）的关系。
\item[心态的云堡] 在其稀薄的空气中，你将会了解 Lisp
和函数式编程的意义和方法。你将Clojure 中渗透的简洁哲学，以及如何像一个
Clojure 程序员那样解决问题。
\end{description}    
}

\colchunk{
    \begin{description}
        \item [The Forest of Tooling] A friendly and \csh一音标{Efficient}{/ɪˈfɪʃənt/：高效的} programming
environment makes it easy to try your ideas. You'll learn how to set up
your environment.
        \item[The Mountain of Language] As you \csh一音标{Ascend}{/əˈsɛnd/：攀登}, you'll \csh一音标{Gain}{/ɡeɪn/：获取} knowledge
of Clojure's syntax, \csh一音标{Semantics}{/sɪˈmæntɪks/：语义}, and data structures. You'll learn how to
use one of the \csh一音标{Mightiest}{/ˈmaɪtɪəst/：最强大的} programming tools, the macro, and learn how to
simplify your life with Clojure's \csh一音标{Concurrency}{/kənˈkɜːrənsi/：并发} constructs.
\item[The Cave of Artifacts] In its depths you'll learn to build, run,
and \csh一音标{Distribute}{/dɪˈstrɪbjuːt/：分发} your own programs, and how to use code libraries. You'll
also learn Clojure's relationship to the Java Virtual Machine (JVM).
\item[The Cloud Castle of Mindset] In its \csh一音标{Rarefied}{/ˈrɛrɪfaɪd/：稀薄的} air, you'll come to
know the why and how of Lisp and functional programming. You'll learn
about the \csh一音标{Philosophy}{/fɪˈlɑːsəfi/：哲学} of simplicity that \csh一音标{Permeates}{/ˈpɜːrmiːts/：渗透} Clojure, and how to
solve problems like a Clojurist.
    \end{description}
}
\end{parcolumns}


这段话介绍了 Clojure 编程语言独特的心态方式。在 Clojure
中，程序员应该专注于\textbf{问题的本质}，而不是关注实现细节。Clojure
也强调简洁和优雅的代码风格。

\begin{parcolumns}[colwidths={1=\parcolumnsLeft}]{2}% 设置为两栏排版
\colchunk{学习 Clojure
需要付出努力，但这本书将让学习过程充满乐趣，而不是枯燥乏味。这是因为这本书遵循以下三个准则：}
\colchunk{Make no mistake, you will work. But this book will make the work feel
\csh一音标{exhilarating}{/ɪgˈzɪləreɪtɪŋ/ 令人兴奋的}, not \csh一音标{exhausting}{/ɪgˈzɔːstɪŋ/ 使人疲惫的，耗尽的}. That's because this book follows three
\csh一音标{guidelines}{/ˈɡaɪdlaɪnz/ 准则}:}
\end{parcolumns}

\begin{parcolumns}[colwidths={1=\parcolumnsLeft}]{2}% 设置为两栏排版
\colchunk{
    \begin{itemize}
        \item 它采取了``甜品先行''的方法，为你提供开发工具和语言细节，使你能\textbf{立即开始实践真实的程序}。
        \item 它假定你对JVM、函数式编程或Lisp没有任何经验。它详细介绍了这些主题，所以当你构建和运行Clojure程序时，你会对自己正在做的事情感到自信。
        \item 它避免使用现实世界的例子，而选择更有趣的练习，例如攻击霍比特人和追踪闪闪发光的吸血鬼。
    \end{itemize}
}
\colchunk{
    \begin{itemize}
        \item It takes the \csh一音标{dessert}{/dɪˈzɜːrt/ 甜点}-first \csh一音标{approach}{/əˈprəʊtʃ/ 方法，方式}, giving you the development tools
        and language details you need to start playing with real programs
        immediately.
        \item It assumes zero \csh一音标{experience}{/ɪkˈspɪəriəns/ 经验} with the JVM, functional programming, or
Lisp. It covers these topics in detail so you'll feel \csh一音标{confident}{/ˈkɒnfɪdənt/ 自信的} about
what you're doing when you build and run Clojure programs.
\item It \csh一音标{eschews}{/ɪˈʃuːz/ 避开，放弃} \emph{real-world} examples in \csh一音标{favor}{/ˈfeɪvər/ 支持，喜爱} of more interesting
exercises, like \emph{\csh一音标{assaulting}{/əˈsɔːltɪŋ/ 攻击} hobbits} and \emph{tracking \csh一音标{glittery}{/ˈɡlɪtəri/ 闪闪发光的~/ˈvæmpaɪərz/ 吸血鬼}
vampires}.
    \end{itemize}
}
\end{parcolumns}