% !TeX root = tcolorbox.tex
% include file of tcolorbox.tex (manual of the LaTeX package tcolorbox)
%  

% \include*{fitting/fitting}
% \include*{fitting/库中的宏}

% \include*{fitting/库的选项键}





\begin{docTcbKey}{fit maxfontdiff}{=\meta{dimension}}{no default, initially |0.1pt|}
The algorithm stops, if the font size is determined within a deviation of
\meta{dimension}.

如果字体大小在 \meta{dimension} 的偏差范围内确定，则算法停止。
\end{docTcbKey}


\begin{docTcbKey}{fit maxfontdiffgap}{=\meta{dimension}}{no default, initially |1pt|}
The algorithm stops, if the number of lines is determined and the font size is
determined within a deviation of \meta{dimension}.

如果行数已确定并且字体大小在 \meta{dimension} 的偏差范围内确定，则算法停止。
\end{docTcbKey}


\begin{docTcbKey}{fit maxwidthdiff}{=\meta{dimension}}{no default, initially |1pt|}
The algorithm stops, if the (optionally) flexible box width
is determined within a deviation of \meta{dimension}.

如果确定了（可选的）灵活框宽度并且其宽度在 \meta{dimension} 的偏差范围内，则算法停止。
\end{docTcbKey}


\begin{docTcbKey}{fit maxwidthdiffgap}{=\meta{dimension}}{no default, initially |10pt|}
The algorithm stops, if the number of lines is determined and the (optionally) flexible box width
is determined within a deviation of \meta{dimension}.

如果行数已确定并且（可选的）灵活框宽度已在 \meta{dimension} 的偏差范围内确定，则算法停止。
\end{docTcbKey}


\begin{docTcbKey}{fit warning}{=\meta{value}}{no default, initially |off|}
Typically, the fit control algorithm constructs several auxiliary boxes
to determine the optimal one. If not switched off, the construction of
the auxiliary boxes may produce many |hbox| warnings. This option key
changes the |\hbadness| value.

通常，适合控制算法构建多个辅助框来确定最佳框。如果没有关闭，构建辅助框可能会产生许多 |hbox| 警告。此选项键更改 |\hbadness| 值。
  \begin{itemize}
  \item\docValue{off}: Most of |`Underfull \hbox'| and |`Overfull \hbox'| warnings are
    switched off (including the ones for the finally used box).

    关闭大部分 |Underfull \hbox'| 和 |Overfull \hbox'| 警告（包括最终使用的框的警告）。
  \item\docValue{on}: All warnings for all auxiliary boxes are displayed.

  显示所有辅助框的所有警告。
  \item\docValue{final}: Only warnings for the finally used box are displayed.
    Note that an additional box has to be contructed for theses messages.

    仅显示最终使用的框的警告。请注意，为这些消息必须构造一个额外的框。
  \end{itemize}
\end{docTcbKey}

\end{document} 