% % !TeX root = tcolorbox.tex
% % include file of tcolorbox.tex (manual of the LaTeX package tcolorbox)
% \clearpage
\section{Library \mylib{documentation}}\label{sec:documentation}%
\tcbset{external/prefix=external/documentation_}%
This library has the single purpose to support \LaTeX\ package documentations
like this one. Actually, the visual nature follows the approach from
Till Tantau's |pgf| \cite{tantau:tikz_and_pgf} documentation.
Typically, this library is assumed to be used in conjunction with the
class |ltxdoc| or alike.
Denis Bitouz\'e, Muzimuzhi, and many others provided very valuable input for this library.

这个库的唯一目的是支持像这个一样的\LaTeX\ 包文档。实际上，其视觉风格遵循了Till Tantau的|pgf|\cite{tantau:tikz_and_pgf}文档的方法。通常，这个库被认为是与类|ltxdoc|或类似的类一起使用的。Denis Bitouz'e，Muzimuzhi和许多其他人为这个库提供了非常有价值的输入。

The library is loaded by a package option or inside the preamble by:

该库可以通过软件包选项或者在导言部分中被加载：
\begin{dispListing}
  \tcbuselibrary{documentation}
\end{dispListing}
This also loads
the library \mylib{skins}, see \Vref{sec:skins},
the library \mylib{raster}, see \Vref{sec:raster},
the library \mylib{listings}, see \Vref{sec:listings},
the library \mylib{xparse}, see \Vref{sec:xparse},
and a bunch of packages, namely
|makeidx|, |marginnote|, |refcount|, and |hyperref|.
The packages |pifont| and |marvosym| should be installed for some symbols, but
need not to be loaded.

这也会加载库\mylib{skins}，参见\Vref{sec:skins}， 库\mylib{raster}，参见\Vref{sec:raster}， 库\mylib{listings}，参见\Vref{sec:listings}， 库\mylib{xparse}，参见\Vref{sec:xparse}， 以及一堆包，即 |makeidx|，|marginnote|，|refcount|和|hyperref|。 对于一些符号，应安装包|pifont|和|marvosym|，但不需要加载。

\begin{marker}
The package |makeidx| is loaded only, if \docAuxCommand*{printindex} is
\emph{not} already defined. Therefore, one can include an alternative to |makeidx| like
|imakeidx| \emph{before} the library |documentation| is used.

只有当\docAuxCommand*{printindex}没有被定义时，才会加载|makeidx|包。因此，在使用库|documentation|之前，可以在其之前包含一个替代|makeidx|的包，例如|imakeidx|。
\end{marker}
\begin{marker}
The package |marginnote| is loaded only, if \docAuxCommand*{marginnote} is
\emph{not} already defined.

只有当 \docAuxCommand*{marginnote} 没有被定义时，才会加载 |marginnote| 包。
\end{marker}
\begin{marker}
In contrast to other |tcolorbox| options, the option
settings for \mylib{documentation} are typically not
getting reset by \refKeyLe{/tcb/reset}, i.e. they keep their
values for embedded boxes.

与其他 |tcolorbox| 选项不同的是，\mylib{documentation} 的选项设置通常不会被 \refKeyLe{/tcb/reset} 重置，即它们会保持嵌入箱子的值不变。
\end{marker}
\begin{marker}
In combination with DocStrip, \refKeyLe{/tcb/verbatim ignore percent} may be helpful.

结合使用DocStrip，\refKeyLe{/tcb/verbatim ignore percent}可能会有所帮助。
\end{marker}

For UTF-8 support load (ignore this when using Xe\LaTeX):

对于UTF-8支持加载（当使用Xe\LaTeX 时请忽略此项）：
\begin{dispListing}
  \tcbuselibrary{listingsutf8,documentation}
\end{dispListing}

For |minted| \cite{poore:minted} support, load:

要使用 |minted| \cite{poore:minted}，请加载以下内容：
\begin{dispListing}
  \tcbuselibrary{documentation,minted}
  \tcbset{listing engine=minted}
\end{dispListing}


%% todo 以上后面放开

%\clearpage
%-------------------------------------------------------------------------------
\subsection{Macros of the Library\\库的宏}
\input{documentation/库的宏}

\clearpage
%-------------------------------------------------------------------------------
\subsection{Entry Content Option Keys\\条目内容选项键}
\input{documentation/条目内容选项键}


\clearpage
%-------------------------------------------------------------------------------
\subsection{Entry Customization Option Keys\\条目自定义选项键}
\input{documentation/条目自定义选项键}

\clearpage
\subsection{General Customization Option Keys\\常规自定义选项键}
\input{documentation/常规自定义选项键}



% \clearpage
% %-------------------------------------------------------------------------------
\subsection{Language Option Keys\\语言选项键}
\input{documentation/语言选项键}

% \clearpage



\subsection{Predefined Colors of the Library\\库中预定义的颜色}\tcbdocmarginnote{\tcbdocupdated{2019-09-18}}
The following colors are predefined. They are used as default colors
in some library commands.

以下颜色是预定义的。它们在某些库命令中用作默认颜色。

\def\dispColor#1{\docColor{#1}~\tikz[baseline=1mm]\path[fill=#1,draw] (0,0) rectangle (0.4,0.4);~}

\dispColor{Option},
\dispColor{Definition},
\dispColor{ExampleFrame},
\dispColor{ExampleBack},
\dispColor{Hyperlink},
\dispColor{Fade}.


