% !TeX root = tcolorbox.tex
% include file of tcolorbox.tex (manual of the LaTeX package tcolorbox)
% \clearpage
% Side by Side

\setcounter{section}{5}
\setcounter{subsection}{2}

\section{并排}\label{sec:sidebyside}%
\tcbset{external/prefix=external/sidebyside_}%

A \csh渐变盒子{side by side} box is a special \refEnvLe{tcolorbox} where
the upper and lower part of the box are set side by side.
All boxes of this kind are unbreakable.


一个\emph{并排}的盒子是一个特殊的\refEnvLe{tcolorbox}，其中盒子的上部和下部并排设置。这种类型的所有盒子都是\csh渐变盒子[red]{不可分割的}。


\begin{marker}
% \begin{stripedbox}
Further side by side options for code examples are
% \tcblower

进一步的排版代码的 side by side 选项的例子有
% \end{stripedbox}

\refKeyLe{/tcb/listing side text},
\refKeyLe{/tcb/text side listing},
\refKeyLe{/tcb/listing outside text}, 和
\refKeyLe{/tcb/text outside listing}.
\end{marker}

% Basic Settings \hfill 
\subsection{基本设置}\label{subsec:sidebyside_basic}

% \input{sidebyside/key_sidebyside}%
% \input{sidebyside/key_sidebyside_align.tex}%
% \input{sidebyside/key_sidebyside_gap.tex}%
% \input{sidebyside/key_lefthand_righthand_etc.tex}% % code={\sbox{\mysavebox}{#2}}, % lefthand width=\wd\mysavebox, 学习了

% \input{sidebyside/cmd_tcbsidebyside.tex}%\subsection{来自\mylib{xparse}库的高级设置}
\input{sidebyside/key_sidebyside_adapt.tex}

 




 
\end{document}

 


% \clearpage
\begin{docTcbKey}[][doc new=2015-11-20]{sidebyside switch}{\colOpt{=true\textbar false}}{default |true|, initially |false|}
\begin{stripedbox}
If set to |true|, the
\meta{left-handed content} and \meta{right-handed content}
of \refComLe{tcbsidebyside} are switched.
Obviously, this option is only valid inside \refComLe{tcbsidebyside}.
\tcblower
如果设置为|true|,%
\refComLe{tcbsidebyside}的 \meta{left-handed content} 和 \meta{right-handed content} 会被切换。%
显然，这个选项只在\refComLe{tcbsidebyside}内有效。
\end{stripedbox}

\begin{stripedbox}
The side switching can be made even/odd page sensitive, 
if used inside \refKeyLe{/tcb/if odd page}.
\tcblower
如果指定了了 \refKeyLe{/tcb/if odd page}，两侧切换对奇/偶页敏感。
\end{stripedbox}


\begin{dispExample}
% \tcbuselibrary{skins,xparse}
\tcbsidebyside{Left}{Right}

\tcbsidebyside[sidebyside switch]{Left}{Right}

\tcbsidebyside[title=Very important table,
  if odd page={sidebyside switch,sidebyside adapt=right,flushright title}%
              {sidebyside adapt=left},
  beamer,colframe=blue!50!black,colback=blue!10,
  lower separated=false,sidebyside gap=5mm
]{%
  \begin{tabular}{|l|c|r|}\hline
    left & center & right\\\hline
    A & B & C\\\hline
    D & E & F\\\hline
  \end{tabular}
}{%
  This table contains the most important figures for
  all future actions. You may notice that B follows A,
  C follows B, and so on.
}
\end{dispExample}


\end{docTcbKey}

