\columnratio{0.55}
\begin{paracol}{2}
\subsection{A minimal file}\label{uAMinimalFile}
\switchcolumn
\subsection{一个最小的文件}
\switchcolumn[0]*%%%%%%%%%%%%
Before using the \packagename{listings} package, you should be familiar with
the \LaTeX\ typesetting system. You need not to be an expert.
Here is a minimal file for \packagename{listings}.
\switchcolumn
在使用\packagename{listings}宏包之前，您应该熟悉\LaTeX 排版系统。您不需要成为专家。下面是一个\packagename{listings}宏包的最小文件示例。
\switchcolumn[0]*%%%%%%%%%%%%
\begin{verbatim}
    % \documentclass{article}
    % \usepackage{listings}

    % \begin{document}
    % \lstset{language=Pascal}

    %   % Insert Pascal examples here.

    % \end{document}\end{verbatim}
\switchcolumn
\begin{verbatim}
    % \documentclass{article}
    % \usepackage{listings}

    % \begin{document}
    % \lstset{language=Pascal}

    % % 在此处插入Pascal示例代码。

    % \end{document}\end{verbatim}
\switchcolumn[0]*%%%%%%%%%%%%
Now type in this first example and run it through \LaTeX.
\switchcolumn
现在输入这个第一个示例并运行它通过\LaTeX。
\end{paracol}




\begin{advise}
\begin{paracol}{2}    
\item Must I do that really?
    \advisespace
    Yes and no. Some books about programming say this is good.
    What a mistake! Typing takes time---which is wasted if the code is clear to
    you. And if you need that time to understand what is going on, the
    author of the book should reconsider the concept of presenting the
    crucial things---you might want to say that about this guide even---or
    you're simply inexperienced with programming. If only the latter case
    applies, you should spend more time on reading (good) books about
    programming, (good) documentations, and (good) source code from other
    people. Of course you should also make your own experiments.
    You will learn a lot. However, running the example through \LaTeX\
    shows whether the \packagename{listings} package is installed correctly.
    \switchcolumn
    \item 我真的需要这样做吗？
    \advisespace
    既是又非。有些关于编程的书籍说这样做是好的。这是一个错误！输入需要时间，如果代码对您来说很清晰，那么这些时间就是浪费的。如果您需要时间来理解正在发生的事情，那么书的作者应该重新考虑介绍关键内容的概念---甚至可能会对这个指南说出这样的话---或者您对编程经验不够丰富。如果只是后一种情况，您应该花更多时间阅读（好的）关于编程的书籍，（好的）文档和其他人的（好的）源代码。当然，您也应该进行自己的实验。您将学到很多。然而，通过\LaTeX 运行示例可以显示\packagename{listings}宏包是否正确安装。
\switchcolumn[0]*
\item The example doesn't work.
    \advisespace
    Are the two packages \packagename{listings} and \packagename{keyval}
    installed on your system? Consult the administration tool of your
    \TeX\ distribution, your system administrator, the local \TeX\ and
    \LaTeX\ guides, a \TeX\ FAQ, and section \ref{rInstallation}---in
    that order. If you've checked \emph{all} these sources and are
    still helpless, you might want to write a post to a \TeX\ newsgroup
    like \texttt{comp.text.tex}.
    \switchcolumn
    \item 这个示例不起作用。
    \advisespace
    您的系统上是否安装了两个包\packagename{listings}和\packagename{keyval}？请查阅您的\TeX 发行版的管理工具、系统管理员、本地\TeX 和\LaTeX 指南、\TeX 常见问题解答，并按照这个顺序查找。如果您已经检查了\emph{所有}这些来源，仍然无助，您可能想在\TeX 新闻组（如\texttt{comp.text.tex}）上发布一篇帖子。
    \switchcolumn[0]*    
\item Should I read the software license before using the package?
    \advisespace
    Yes, but read this \emph{Getting started} section first to decide
    whether you are willing to use the package.^^A ;-)
    \switchcolumn
    \item 在使用该宏包之前，我应该阅读软件许可证吗？
\advisespace
是的，但在使用该宏包之前，请先阅读本“入门”部分，以决定您是否愿意使用该宏包。^^A ;-)
\end{paracol}
\end{advise}